---
title: "Survey data summary"
author: "EWilliams"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
#
# Set data type working with (based on database coding) and initials 
Data_type <- c("SRVY")
Initials <- c("ELW")
#
#
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
#Load packages, install as needed
#if (!require("remotes")) install.packages("remotes") pacman::p_unlock()
if (!require("pacman")) {install.packages("pacman")}
pacman::p_load(plyr, tidyverse, glue, purrr, #Df manipulation, 
               ggpubr, scales, lemon, ggnewscale, gt, #ploting, tables
               rstatix, broom, #Summary stats
               zoo, lubridate, forecast, #Dates and times
               readxl, #Reading excel files
               car, emmeans, multcomp, #Basic analyses
               lmPerm, stats, glmmTMB, AICcmodavg, DHARMa, performance,
               install = TRUE)

```

```{r Formatting, include=FALSE}
#
# Establish consistent formatting for plots:
basetheme <- theme_bw()+
        # Set axis title and text parameters
  theme(axis.title.x = element_text(size = 12, face = "bold", color = "black"), 
        axis.text.x = element_text(size = 11, margin = margin(t=0.5, l=0.5, r=0, b=0.15, unit = "cm")),
        axis.title.y = element_text(size = 12, face = "bold", color = "black"), 
        axis.text.y = element_text(size = 11, margin = margin(t=0, l=0.25, r=0, b=0, unit = "cm")),
        # Remove grid lines and box around plot
        panel.grid = element_blank(), 
        panel.border = element_blank(), 
        # Modify axes
        axis.line = element_line(color = "black"),
        axis.ticks.length = unit(-0.15, "cm"))
#
#
```

```{r Load data files, include=FALSE}

## Fixed Locations
FLID_raw <- read_excel("../Data/Srvy_data_clean_ELW.xlsx", sheet = "FLIDs", 
                       skip = 0, col_names = TRUE,  
                       na = c("", "NULL", " ", "NAN", "na"), trim_ws = TRUE, 
                       .name_repair = "unique") 
#
## Survey
Quads_raw <- read_excel("../Data/Srvy_data_clean_ELW.xlsx", sheet = "Quadrats", 
                       skip = 0, col_names = TRUE,  
                       na = c("", "NULL", " ", "NAN", "na"), trim_ws = TRUE, 
                       .name_repair = "unique") 
#
## Survey SHs
SHs_raw <- read_excel("../Data/Srvy_data_clean_ELW.xlsx", sheet = "ShellHeights", 
                        skip = 0, col_names = TRUE,  
                        na = c("", "NULL", " ", "NAN", "na"), trim_ws = TRUE, 
                        .name_repair = "unique") 
#
```

```{r Data summary, include=FALSE}

## Survey counts
Quads_df <- Quads_raw %>%
  # Group by all columns needed to keep
  group_by(Lab, SrvyType, 
           Date, Year, Month, Quarter,
           Estuary, SectionName, StationName, StationNumber,
           QuadratNumber) %>%
  # Determine mean Live, Dead, and DeadRatio per quadrat
  summarise(Live = mean(TotalLive, na.rm = T),
            Dead = mean(TotalDead, na.rm = T),
            DeadRatio = mean(DeadRatio, na.rm = T),
            .groups = "drop")
#
#
#
## Mean survey counts per station (as rep) divided by Fixed or Random surveys
Fixed_counts <- Quads_df %>% 
  filter(SrvyType == "Fixed") 
#
Random_counts <- Quads_df %>% 
  filter(SrvyType == "Random")
#
### Annual summaries:
Fixed_Annual_summ <- Fixed_counts %>%
  # Group by all columns needed in data output
  group_by(Lab, Estuary, Year) %>%
  summarise(Samples = n(),
            # Live
            meanLive = mean(Live, na.rm = TRUE),
            sdLive = sd(Live, na.rm = TRUE),
            seLive   = sdLive / sqrt(n()),
            minLive = min(Live, na.rm = TRUE),
            maxLive = max(Live, na.rm = TRUE),
            # Dead
            meanDead = mean(Dead, na.rm = TRUE),
            sdDead = sd(Dead, na.rm = TRUE),
            seDead   = sdDead / sqrt(n()),
            minDead = min(Dead, na.rm = TRUE),
            maxDead = max(Dead, na.rm = TRUE),
            # Dead Ratio
            meanDeadRatio = mean(DeadRatio, na.rm = TRUE),
            sdDeadRatio = sd(DeadRatio, na.rm = TRUE),
            seDeadRatio   = sdDeadRatio / sqrt(n()),
            minDeadRatio = min(DeadRatio, na.rm = TRUE),
            maxDeadRatio = max(DeadRatio, na.rm = TRUE),
            .groups = "drop")
#
Random_Annual_summ <- Random_counts %>%
  # Group by all columns needed in data output
  group_by(Lab, Estuary, Year) %>%
  summarise(Samples = n(),
            # Live
            meanLive = mean(Live, na.rm = TRUE),
            sdLive = sd(Live, na.rm = TRUE),
            seLive   = sdLive / sqrt(n()),
            minLive = min(Live, na.rm = TRUE),
            maxLive = max(Live, na.rm = TRUE),
            # Dead
            meanDead = mean(Dead, na.rm = TRUE),
            sdDead = sd(Dead, na.rm = TRUE),
            seDead   = sdDead / sqrt(n()),
            minDead = min(Dead, na.rm = TRUE),
            maxDead = max(Dead, na.rm = TRUE),
            # Dead Ratio
            meanDeadRatio = mean(DeadRatio, na.rm = TRUE),
            sdDeadRatio = sd(DeadRatio, na.rm = TRUE),
            seDeadRatio   = sdDeadRatio / sqrt(n()),
            minDeadRatio = min(DeadRatio, na.rm = TRUE),
            maxDeadRatio = max(DeadRatio, na.rm = TRUE),
            .groups = "drop")
#
#
#
### Section summaries:
Fixed_Section_summ <- Fixed_counts %>%
  # Group by all columns needed in data output
  group_by(Lab, Estuary, SectionName) %>%
  summarise(Samples = n(),
            # Live
            meanLive = mean(Live, na.rm = TRUE),
            sdLive = sd(Live, na.rm = TRUE),
            seLive   = sdLive / sqrt(n()),
            minLive = min(Live, na.rm = TRUE),
            maxLive = max(Live, na.rm = TRUE),
            # Dead
            meanDead = mean(Dead, na.rm = TRUE),
            sdDead = sd(Dead, na.rm = TRUE),
            seDead   = sdDead / sqrt(n()),
            minDead = min(Dead, na.rm = TRUE),
            maxDead = max(Dead, na.rm = TRUE),
            # Dead Ratio
            meanDeadRatio = mean(DeadRatio, na.rm = TRUE),
            sdDeadRatio = sd(DeadRatio, na.rm = TRUE),
            seDeadRatio   = sdDeadRatio / sqrt(n()),
            minDeadRatio = min(DeadRatio, na.rm = TRUE),
            maxDeadRatio = max(DeadRatio, na.rm = TRUE),
            .groups = "drop")
#
Random_Section_summ <- Random_counts %>%
  # Group by all columns needed in data output
  group_by(Lab, Estuary, SectionName) %>%
  summarise(Samples = n(),
            # Live
            meanLive = mean(Live, na.rm = TRUE),
            sdLive = sd(Live, na.rm = TRUE),
            seLive   = sdLive / sqrt(n()),
            minLive = min(Live, na.rm = TRUE),
            maxLive = max(Live, na.rm = TRUE),
            # Dead
            meanDead = mean(Dead, na.rm = TRUE),
            sdDead = sd(Dead, na.rm = TRUE),
            seDead   = sdDead / sqrt(n()),
            minDead = min(Dead, na.rm = TRUE),
            maxDead = max(Dead, na.rm = TRUE),
            # Dead Ratio
            meanDeadRatio = mean(DeadRatio, na.rm = TRUE),
            sdDeadRatio = sd(DeadRatio, na.rm = TRUE),
            seDeadRatio   = sdDeadRatio / sqrt(n()),
            minDeadRatio = min(DeadRatio, na.rm = TRUE),
            maxDeadRatio = max(DeadRatio, na.rm = TRUE),
            .groups = "drop")
#
#
### Annual x Section summaries:
Fixed_Ann_Sec_summ <- Fixed_counts %>%
                   # Group by all columns needed in data output
                   group_by(Lab, Estuary, Year, SectionName) %>%
                   summarise(Samples = n(),
            # Live
            meanLive = mean(Live, na.rm = TRUE),
            sdLive = sd(Live, na.rm = TRUE),
            seLive   = sdLive / sqrt(n()),
            minLive = min(Live, na.rm = TRUE),
            maxLive = max(Live, na.rm = TRUE),
            # Dead
            meanDead = mean(Dead, na.rm = TRUE),
            sdDead = sd(Dead, na.rm = TRUE),
            seDead   = sdDead / sqrt(n()),
            minDead = min(Dead, na.rm = TRUE),
            maxDead = max(Dead, na.rm = TRUE),
            # Dead Ratio
            meanDeadRatio = mean(DeadRatio, na.rm = TRUE),
            sdDeadRatio = sd(DeadRatio, na.rm = TRUE),
            seDeadRatio   = sdDeadRatio / sqrt(n()),
            minDeadRatio = min(DeadRatio, na.rm = TRUE),
            maxDeadRatio = max(DeadRatio, na.rm = TRUE),
            .groups = "drop")
#
#
Random_Ann_Sec_summ <- Random_counts %>%
                   # Group by all columns needed in data output
                   group_by(Lab, Estuary, Year, SectionName) %>%
                   summarise(Samples = n(),
            # Live
            meanLive = mean(Live, na.rm = TRUE),
            sdLive = sd(Live, na.rm = TRUE),
            seLive   = sdLive / sqrt(n()),
            minLive = min(Live, na.rm = TRUE),
            maxLive = max(Live, na.rm = TRUE),
            # Dead
            meanDead = mean(Dead, na.rm = TRUE),
            sdDead = sd(Dead, na.rm = TRUE),
            seDead   = sdDead / sqrt(n()),
            minDead = min(Dead, na.rm = TRUE),
            maxDead = max(Dead, na.rm = TRUE),
            # Dead Ratio
            meanDeadRatio = mean(DeadRatio, na.rm = TRUE),
            sdDeadRatio = sd(DeadRatio, na.rm = TRUE),
            seDeadRatio   = sdDeadRatio / sqrt(n()),
            minDeadRatio = min(DeadRatio, na.rm = TRUE),
            maxDeadRatio = max(DeadRatio, na.rm = TRUE),
            .groups = "drop")
#
#
# 
#
#
#
```

# Background
Survey data any time of year is included in comparisons. Surveys are divided by "Fixed" and "Random" for comparisons.\
Fixed = planned repeated sampling stations\
Random = single sampling event or station that is selected randomly for survey and has the potential for re-sampling if same station is selected across time\
\

# Fixed location surveys
```{r Fixed Estuary annual summary, echo = FALSE, results ="asis"}
paste("List of sites included:")
cat("<br>")
unique(Fixed_Annual_summ$Estuary)
#
Fixed_Annual_summ %>% ungroup() %>%
  dplyr::select(Estuary, Year) %>%
  group_by(Estuary, Year) %>%
  summarise(Count = n()) %>%
  arrange(Year) %>%
  pivot_wider(names_from = "Year", values_from = "Count") %>%
  ungroup()%>%
  gt() %>%
  sub_missing(missing_text = "")
#
#
```

## Statewide

```{r Fixed Estuary summary, echo = FALSE, fig.align='center', results ="asis"}
#
# Filter to Estuary:
All_Fixed_summ <- Fixed_counts %>%
  # Group by all columns needed in data output
  group_by(Estuary) %>%
  summarise(Samples = n(),
            # Live
            meanLive = mean(Live, na.rm = TRUE),
            sdLive = sd(Live, na.rm = TRUE),
            seLive   = sdLive / sqrt(n()),
            minLive = min(Live, na.rm = TRUE),
            maxLive = max(Live, na.rm = TRUE),
            # Dead
            meanDead = mean(Dead, na.rm = TRUE),
            sdDead = sd(Dead, na.rm = TRUE),
            seDead   = sdDead / sqrt(n()),
            minDead = min(Dead, na.rm = TRUE),
            maxDead = max(Dead, na.rm = TRUE),
            # Dead Ratio
            meanDeadRatio = mean(DeadRatio, na.rm = TRUE),
            sdDeadRatio = sd(DeadRatio, na.rm = TRUE),
            seDeadRatio   = sdDeadRatio / sqrt(n()),
            minDeadRatio = min(DeadRatio, na.rm = TRUE),
            maxDeadRatio = max(DeadRatio, na.rm = TRUE),
            .groups = "drop")


## Live counts
# Annual means table
All_Fixed_summ %>%
  ungroup() %>%
  dplyr::select(Estuary,
                `Mean` = meanLive,
                `SE` = seLive) %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Average live oyster density")

# Annual means comps
model_data <- Fixed_counts %>% 
  mutate(Estuary = as.factor(Estuary)) %>% 
  group_by(Estuary, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$Year) > 1) {
  set.seed(54321)
  F_All_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ Estuary + (1|Year), family = nbinom2, data = model_data))
} else {
  cat("Only one survey year is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("F_All_model") && !is.null(F_All_model)){
  F_All_model_tab <<- car::Anova(F_All_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  F_All_cld <- suppressMessages(
    suppressWarnings(
      left_join(F_All_summ, 
                multcomp::cld(
                  emmeans(F_All_model, ~ Estuary, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(Estuary, Group))
      ))
  
   p <- F_All_cld %>%
        ggplot(aes(Estuary, meanLive, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        geom_text(aes(y = meanLive + seLive, label = Group), vjust = -1, color = "black")+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme
   
  } else {
     p <- F_All_summ %>%
        ggplot(aes(Estuary, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme 
  }
#
#
if(exists("F_All_model_tab")){
  F_All_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Estuary model results")
}

p

## Summary info
F_All_min <- F_All_summ %>% slice_min(meanLive, n = 1, with_ties = TRUE)
F_All_max <- F_All_summ %>% slice_max(meanLive, n = 1, with_ties = TRUE)
F_All_mean <- F_All_summ %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("F_All_model_tab")){
  pValue <- car::Anova(F_All_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
cat("<br><br><br><br>") 
## Dead ratio
# Annual means table
All_Fixed_summ %>%
  ungroup() %>%
  dplyr::select(Estuary,
                `Mean` = meanDeadRatio,
                `SE` = seDeadRatio) %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Average dead ratio")

# Annual means comps
DR_model_data <- Fixed_counts %>% 
  mutate(Estuary = as.factor(Estuary)) %>% 
  group_by(Estuary, Year) %>%
  summarise(MeanDeadRatio = mean(DeadRatio, na.rm =T),
            .groups = "drop") %>%
  mutate(MeanDR = (MeanDeadRatio * (n() - 1) + 0.5) / n()) %>% #transformation to make (0,1)
  droplevels()
#
if (dplyr::n_distinct(DR_model_data$Year) > 1) {
  set.seed(54321)
  DR_model <- suppressWarnings(glmmTMB::glmmTMB(MeanDR ~ Estuary + (1|Year), family = beta_family(link = "logit"), data = DR_model_data))
} else {
  cat("Only one survey year is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("DR_model") && !is.null(DR_model)){
  DR_model_tab <<- car::Anova(DR_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  DR_cld <- suppressMessages(
    suppressWarnings(
      left_join(All_summ, 
                multcomp::cld(
                  emmeans(DR_model, ~ Estuary, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(Estuary, Group))
      ))
  
   p <- DR_cld %>%
        ggplot(aes(Estuary, meanDeadRatio, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanDeadRatio, ymax = meanDeadRatio + seDeadRatio), width = 0.25)+
        geom_text(aes(y = meanDeadRatio + seDeadRatio, label = Group), vjust = -1, color = "black")+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average dead ratio per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme
   
  } else {
     p <- All_summ %>%
        ggplot(aes(Estuary, meanDeadRatio))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanDeadRatio, ymax = meanDeadRatio + seDeadRatio), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average dead ratio per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme 
  }
#
#
if(exists("DR_model_tab")){
  DR_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Estuary model results")
}

p

## Summary info
DR_min <- All_summ %>% slice_min(meanDeadRatio, n = 1, with_ties = TRUE)
DR_max <- All_summ %>% slice_max(meanDeadRatio, n = 1, with_ties = TRUE)
DR_mean <- All_summ %>% ungroup() %>% summarise(mean = mean(meanDeadRatio, na.rm = T),
                                               sd = sd(meanDeadRatio, na.rm = T))
if(exists("DR_model_tab")){
  pValueDR <- car::Anova(DR_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValueDR <- NULL
}
#
#
#
```
\
\
**Summary:**
The mean number of live oysters surveyed ranged from `r round(All_min$meanLive,1)` oysters/m2 in `r All_min$Estuary` to `r round(All_max$meanLive,1)` oysters/m2 in `r All_max$Estuary` with an overall average of `r round(All_mean$mean,1)` +/- `r round(All_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among estuaries `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\
The mean dead ratio of oysters surveyed ranged from `r round(DR_min$meanDeadRatio,1)` in `r DR_min$Estuary` to `r round(DR_max$meanDeadRatio,1)` in `r DR_max$Estuary` with an overall average of `r round(DR_mean$mean,1)` +/- `r round(DR_mean$sd, 1)`. Mean dead ratio `r if(!is.null(pValueDR) && pValueDR$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among estuaries `r if(!is.null(pValueDR) && pValueDR$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValueDR)){""} else {paste0("(p = ",round(pValueDR$p.value[2], 3), ")")}`.
\
\

```{r All estuaries annual plot,  echo = FALSE, fig.align='center', results='asis'}
Annual_summ %>%
  group_by(Year, Estuary) %>%
  summarise(mean = mean(meanLive, na.rm = T),
            sd = sd(meanLive, na.rm = T)) %>%
  ggplot(aes(Year, mean, group = Estuary))+
  geom_line(aes(color = Estuary), linewidth = 1.5)+
  scale_x_discrete(expand = c(0.01,0.1))+
  scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
  scale_colour_viridis_d(option = "H")+
  ggtitle("Annual mean oysters/m2 per estuary")+
  basetheme + theme(axis.text.x = element_text(angle = 45))
cat("<br><br>")
Annual_summ %>%
  group_by(Year, Estuary) %>%
  summarise(mean = mean(meanDeadRatio, na.rm = T),
            sd = sd(meanDeadRatio, na.rm = T)) %>%
  ggplot(aes(Year, mean, group = Estuary))+
  geom_line(aes(color = Estuary), linewidth = 1.5)+
  scale_x_discrete(expand = c(0.01,0.1))+
  scale_y_continuous("Average dead ratio per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
  scale_colour_viridis_d(option = "H")+
  ggtitle("Annual mean dead ratio of oysters per estuary")+
  basetheme + theme(axis.text.x = element_text(angle = 45))
```


# Eastpoint Lab 

## Apalachicola Bay {.tabset}

### Estuary - live

```{r AB estuary summary, echo = FALSE, fig.align='center'}
#
# Filter to Estuary:
AB_summ <- Annual_summ %>% 
  filter(Estuary == "AB") %>%
  droplevels()

# Annual means table
AB_summ %>%
  ungroup() %>%
  dplyr::select(Year,
                `Mean` = meanLive,
                `SE` = seLive) %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Annual live oyster density")

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "AB") %>%
  mutate(Year = as.factor(Year)) %>% 
  group_by(Estuary, SectionName, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$Year) > 1) {
  set.seed(54321)
  AB_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ as.numeric(Year) + (1|SectionName), family = nbinom2, data = model_data))
  AB_model2 <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ Year + (1|SectionName), family = nbinom2, data = model_data))
} else {
  rm(model_data)
  cat("Only one survey year is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("AB_model") && !is.null(AB_model)){
  AB_model_tab <- car::Anova(AB_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  AB_cld <- suppressMessages(
    suppressWarnings(
      left_join(AB_summ, 
                multcomp::cld(
                  emmeans(AB_model2, ~ Year, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(Year, Group))
      ))
  
   p <- AB_cld %>%
        ggplot(aes(Year, meanLive, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
   
  } else {
     p <- AB_summ %>%
        ggplot(aes(Year, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
  }
#
#
if(exists("AB_model_tab")){
  AB_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Annual model results")
}

p

## Summary info
AB_min <- AB_summ %>% group_by(Estuary) %>% slice_min(meanLive, n = 1, with_ties = TRUE)
AB_max <- AB_summ %>% group_by(Estuary) %>% slice_max(meanLive, n = 1, with_ties = TRUE)
AB_mean <- AB_summ %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("AB_model_tab")){
  pValue <- car::Anova(AB_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary:**
The mean number of live oysters surveyed in `r unique(AB_summ$Estuary)` ranged from `r round(AB_min$meanLive,1)` oysters/m2 in `r AB_min$Year` to `r round(AB_max$meanLive,1)` oysters/m2 in `r AB_max$Year` with an overall average of `r round(AB_mean$mean,1)` +/- `r round(AB_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among years `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.

### Sections - live

```{r AB section summary, echo = FALSE, fig.align='center'}
#
# Filter to Estuary:
AB_summ_sec <- Section_summ %>% 
  filter(Estuary == "AB") %>%
  droplevels()

# Annual means table
AB_summ_sec %>%
  ungroup() %>%
  dplyr::select(`Section` = SectionName, 
                `Mean` = meanLive,
                `SE` = seLive) %>%
  #pivot_wider(
  #  names_from = SectionName,
  #  values_from = c(Mean, SE),
  #  names_glue = "{SectionName}_{.value}",
  #  names_vary = "slowest") %>% #Orders columns by SectionName
  gt() %>%
  #tab_spanner_delim(delim = "_") %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Average live oyster density") 

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "AB") %>%
  mutate(across(c(Year, SectionName, StationNumber), as.factor)) %>% 
  group_by(SectionName, StationNumber, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$SectionName) > 1) {
  set.seed(54321)
  AB_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ SectionName + (1|StationNumber), family = nbinom2, data = model_data))
} else {
  rm(model_data)
  cat("Only one estuary section is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("AB_model") && !is.null(AB_model)){
  AB_model_tab <- car::Anova(AB_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  AB_cld <- suppressMessages(
    suppressWarnings(
      left_join(AB_summ_sec, 
                multcomp::cld(
                  emmeans(AB_model, ~ SectionName, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(SectionName, Group))
      ))
  
   p <- AB_cld %>%
        ggplot(aes(SectionName, meanLive, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme
   
  } else {
     p <- AB_summ_sec %>%
        ggplot(aes(SectionName, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme 
  }
#
#
if(exists("AB_model_tab")){
  AB_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Section model results")
}

p

## Summary info
AB_sec_min <- AB_summ_sec %>% slice_min(meanLive, n = 1, with_ties = TRUE)
AB_sec_max <- AB_summ_sec %>% slice_max(meanLive, n = 1, with_ties = TRUE)
AB_sec_mean <- AB_summ_sec %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("AB_model_tab")){
  pValue <- car::Anova(All_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary:**
The mean number of live oysters surveyed in `r unique(AB_summ$Estuary)` ranged from `r round(AB_sec_min$meanLive,1)` oysters/m2 in `r AB_sec_min$SectionName` to `r round(AB_sec_max$meanLive,1)` oysters/m2 in `r AB_sec_max$SectionName` with an overall average of `r round(AB_sec_mean$mean,1)` +/- `r round(AB_sec_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among estuary sections `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\
```{r AB sections annual plot, echo = FALSE, fig.align='center'}
Section_Ann_summ %>%
  filter(Estuary == "AB") %>%
  group_by(Year, SectionName) %>%
  ggplot(aes(Year, meanLive, group = SectionName))+
  geom_line(aes(color = SectionName), linewidth = 1.5)+
  geom_point(aes(color = SectionName), size = 3)+
  scale_x_discrete(expand = c(0.01,0.1))+
  scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
  scale_colour_viridis_d("Section")+
  ggtitle("Annual mean oysters/m2 per section")+
  basetheme + theme(axis.text.x = element_text(angle = 45))
```

### Estuary - dead ratio

```{r AB estuary DR summary, echo = FALSE, fig.align='center'}
#
# Filter to Estuary:
AB_summ <- Annual_summ %>% 
  filter(Estuary == "AB") %>%
  droplevels()

# Annual means table
AB_summ %>%
  ungroup() %>%
  dplyr::select(Year,
                `Mean` = meanDeadRatio,
                `SE` = seDeadRatio) %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Annual dead ratio")

# Annual means comps
DRmodel_data <- Quads_df %>% 
  filter(Estuary == "AB") %>%
  mutate(Year = as.factor(Year)) %>% 
  group_by(Estuary, SectionName, Year) %>%
  summarise(MeanDeadRatio = mean(DeadRatio, na.rm =T),
            .groups = "drop") %>%
  mutate(MeanDR = (MeanDeadRatio * (n() - 1) + 0.5) / n()) %>% #transformation to make (0,1) %>%
  droplevels()
#
if (dplyr::n_distinct(DRmodel_data$Year) > 1) {
  set.seed(54321)
  AB_DR_model <- suppressWarnings(glmmTMB::glmmTMB(MeanDR ~ as.numeric(Year) + (1|SectionName), family = beta_family(link = "logit"), data = DRmodel_data))
  AB_DR_model2 <- suppressWarnings(glmmTMB::glmmTMB(MeanDR ~ Year + (1|SectionName), family = beta_family(link = "logit"), data = DRmodel_data))
} else {
  rm(DRmodel_data)
  cat("Only one survey year is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("AB_DR_model") && !is.null(AB_DR_model)){
  AB_DR_model_tab <- car::Anova(AB_DR_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  AB_DR_cld <- suppressMessages(
    suppressWarnings(
      left_join(AB_summ, 
                multcomp::cld(
                  emmeans(AB_DR_model2, ~ Year, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(Year, Group))
      ))
  
   p <- AB_DR_cld %>%
        ggplot(aes(Year, meanDeadRatio, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanDeadRatio, ymax = meanDeadRatio + seDeadRatio), width = 0.25)+
        geom_text(aes(y = meanDeadRatio + seDeadRatio, label = Group), vjust = -1, color = "black")+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average dead ratio", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
   
  } else {
     p <- AB_summ %>%
        ggplot(aes(Year, meanDeadRatio))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanDeadRatio, ymax = meanDeadRatio + seDeadRatio), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average dead ratio", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
  }
#
#
if(exists("AB_DR-model_tab")){
  AB_DR_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Annual model results")
}

p

## Summary info
AB_DR_min <- AB_summ %>% group_by(Estuary) %>% slice_min(meanDeadRatio, n = 1, with_ties = TRUE)
AB_DR_max <- AB_summ %>% group_by(Estuary) %>% slice_max(meanDeadRatio, n = 1, with_ties = TRUE)
AB_DR_mean <- AB_summ %>% ungroup() %>% summarise(mean = mean(meanDeadRatio, na.rm = T),
                                               sd = sd(meanDeadRatio, na.rm = T))
if(exists("AB_DR_model_tab")){
  pValueDR <- car::Anova(AB_DR_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValueDR <- NULL
}
#
#
```
\
\
**Summary:**
The mean dead ratio of oysters surveyed in `r unique(AB_summ$Estuary)` ranged from `r round(AB_DR_min$meanDeadRatio,1)` in `r AB_DR_min$Year` to `r round(AB_DR_max$meanDeadRatio,1)` in `r AB_DR_max$Year` with an overall average of `r round(AB_DR_mean$mean,1)` +/- `r round(AB_DR_mean$sd, 1)`. Mean dead ratio `r if(!is.null(pValueDR) && pValueDR$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among years `r if(!is.null(pValueDR) && pValueDR$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValueDR)){""} else {paste0("(p = ",round(pValueDR$p.value[2], 3), ")")}`.
\

### {-} 

## Saint Andrews {.tabset}

### Estuary 

```{r SA summary, echo = FALSE, fig.align='center', asis = TRUE}
#
# Filter to Estuary:
SA_summ <- Annual_summ %>% 
  filter(Estuary == "SA") %>%
  droplevels()

# Annual means table
SA_summ %>%
  ungroup() %>%
  dplyr::select(Year,
                `Mean` = meanLive,
                `SE` = seLive) %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Annual live oyster density")

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "SA") %>%
  mutate(Year = as.factor(Year)) %>% 
  group_by(Estuary, SectionName, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$Year) > 1) {
  set.seed(54321)
  SA_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ as.numeric(Year) + (1|SectionName), family = nbinom2, data = model_data))
  SA_model2 <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ Year + (1|SectionName), family = nbinom2, data = model_data))
  } else {
    rm(model_data)
    cat("Only one survey year is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("SA_model") && !is.null(SA_model)){
  SA_model_tab <- car::Anova(SA_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  SA_cld <- suppressMessages(
    suppressWarnings(
      left_join(SA_summ, 
                multcomp::cld(
                  emmeans(SA_model2, ~ Year, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(Year, Group))
      ))
  
   p <- SA_cld %>%
        ggplot(aes(Year, meanLive, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
   
  } else {
     p <- SA_summ %>%
        ggplot(aes(Year, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
  }
#
#
if(exists("SA_model_tab")){
  SA_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Annual model results")
}

p

## Summary info
SA_min <- SA_summ %>% group_by(Estuary) %>% slice_min(meanLive, n = 1, with_ties = TRUE)
SA_max <- SA_summ %>% group_by(Estuary) %>% slice_max(meanLive, n = 1, with_ties = TRUE)
SA_mean <- SA_summ %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("SA_model_tab")){
  pValue <- car::Anova(SA_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary**
The mean number of live oysters surveyed in `r unique(SA_summ$Estuary)` ranged from `r round(SA_min$meanLive,1)` oysters/m2 in `r SA_min$Year` to `r round(SA_max$meanLive,1)` oysters/m2 in `r SA_max$Year` with an overall average of `r round(SA_mean$mean,1)` +/- `r round(SA_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among years `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\

### Sections

```{r SA section summary, echo = FALSE, fig.align='center'}
#
# Filter to Estuary:
SA_summ_sec <- Section_summ %>% 
  filter(Estuary == "SA") %>%
  droplevels()

# Annual means table
SA_summ_sec %>%
  ungroup() %>%
  dplyr::select(`Section` = SectionName, 
                `Mean` = meanLive,
                `SE` = seLive) %>%
  #pivot_wider(
  #  names_from = SectionName,
  #  values_from = c(Mean, SE),
  #  names_glue = "{SectionName}_{.value}",
  #  names_vary = "slowest") %>% #Orders columns by SectionName
  gt() %>%
  #tab_spanner_delim(delim = "_") %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Average live oyster density") 

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "SA") %>%
  mutate(across(c(Year, SectionName, StationNumber), as.factor)) %>% 
  group_by(SectionName, StationNumber, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$SectionName) > 1) {
  set.seed(54321)
  SA_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ SectionName + (1|StationNumber), family = nbinom2, data = model_data))
} else {
  rm(model_data)
  cat("Only one estuary section is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("SA_model") && !is.null(SA_model)){
  SA_model_tab <- car::Anova(SA_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  SA_cld <- suppressMessages(
    suppressWarnings(
      left_join(SA_summ_sec, 
                multcomp::cld(
                  emmeans(SA_model, ~ SectionName, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(SectionName, Group))
      ))
  
   p <- SA_cld %>%
        ggplot(aes(SectionName, meanLive, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme
   
  } else {
     p <- SA_summ_sec %>%
        ggplot(aes(SectionName, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme 
  }
#
#
if(exists("SA_model_tab")){
  SA_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Section model results")
}

p

## Summary info
SA_sec_min <- SA_summ_sec %>% slice_min(meanLive, n = 1, with_ties = TRUE)
SA_sec_max <- SA_summ_sec %>% slice_max(meanLive, n = 1, with_ties = TRUE)
SA_sec_mean <- SA_summ_sec %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("SA_model_tab")){
  pValue <- car::Anova(All_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary:**
The mean number of live oysters surveyed in `r unique(SA_summ$Estuary)` ranged from `r round(SA_sec_min$meanLive,1)` oysters/m2 in `r SA_sec_min$SectionName` to `r round(SA_sec_max$meanLive,1)` oysters/m2 in `r SA_sec_max$SectionName` with an overall average of `r round(SA_sec_mean$mean,1)` +/- `r round(SA_sec_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among estuary sections `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\
```{r SA sections annual plot, echo = FALSE, fig.align='center'}
Section_Ann_summ %>%
  filter(Estuary == "SA") %>%
  ggplot(aes(Year, meanLive, group = SectionName))+
  geom_line(aes(color = SectionName), linewidth = 1.5)+
  geom_point(aes(color = SectionName), size = 3)+
  scale_x_discrete(expand = c(0.01,0.1))+
  scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
  scale_colour_viridis_d("Section")+
  ggtitle("Annual mean oysters/m2 per section")+
  basetheme + theme(axis.text.x = element_text(angle = 45))
```

### {-}

# Crystal River Lab 

## Suwannee Sound {.tabset}

### Estuary 

```{r SS summary, echo = FALSE, fig.align='center', asis = TRUE}
#
# Filter to Estuary:
SS_summ <- Annual_summ %>% 
  filter(Estuary == "SS") %>%
  droplevels()

# Annual means table
SS_summ %>%
  ungroup() %>%
  dplyr::select(Year,
                `Mean` = meanLive,
                `SE` = seLive) %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Annual live oyster density")

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "SS") %>%
  mutate(Year = as.factor(Year)) %>% 
  group_by(Estuary, SectionName, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$Year) > 1) {
  set.seed(54321)
  SS_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ as.numeric(Year) + (1|SectionName), family = nbinom2, data = model_data))
  SS_model2 <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ Year + (1|SectionName), family = nbinom2, data = model_data))
  } else {
    rm(model_data)
    cat("Only one survey year is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("SS_model") && !is.null(SS_model)){
  SS_model_tab <- car::Anova(SS_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  SS_cld <- suppressMessages(
    suppressWarnings(
      left_join(SS_summ, 
                multcomp::cld(
                  emmeans(SS_model2, ~ Year, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(Year, Group))
      ))
  
   p <- SS_cld %>%
        ggplot(aes(Year, meanLive, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
   
  } else {
     p <- SS_summ %>%
        ggplot(aes(Year, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
  }
#
#
if(exists("SS_model_tab")){
  SS_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Annual model results")
}

p

## Summary info
SS_min <- SS_summ %>% group_by(Estuary) %>% slice_min(meanLive, n = 1, with_ties = TRUE)
SS_max <- SS_summ %>% group_by(Estuary) %>% slice_max(meanLive, n = 1, with_ties = TRUE)
SS_mean <- SS_summ %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("SS_model_tab")){
  pValue <- car::Anova(SS_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary**
The mean number of live oysters surveyed in `r unique(SS_summ$Estuary)` ranged from `r round(SS_min$meanLive,1)` oysters/m2 in `r SS_min$Year` to `r round(SS_max$meanLive,1)` oysters/m2 in `r SS_max$Year` with an overall average of `r round(SS_mean$mean,1)` +/- `r round(SS_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among years `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\

### Sections

```{r SS section summary, echo = FALSE, fig.align='center'}
#
# Filter to Estuary:
SS_summ_sec <- Section_summ %>% 
  filter(Estuary == "SS") %>%
  droplevels()

# Annual means table
SS_summ_sec %>%
  ungroup() %>%
  dplyr::select(`Section` = SectionName, 
                `Mean` = meanLive,
                `SE` = seLive) %>%
  #pivot_wider(
  #  names_from = SectionName,
  #  values_from = c(Mean, SE),
  #  names_glue = "{SectionName}_{.value}",
  #  names_vary = "slowest") %>% #Orders columns by SectionName
  gt() %>%
  #tab_spanner_delim(delim = "_") %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Average live oyster density") 

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "SS") %>%
  mutate(across(c(Year, SectionName, StationNumber), as.factor)) %>% 
  group_by(SectionName, StationNumber, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$SectionName) > 1) {
  set.seed(54321)
  SS_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ SectionName + (1|StationNumber), family = nbinom2, data = model_data))
} else {
  rm(model_data)
  cat("Only one estuary section is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("SS_model") && !is.null(SS_model)){
  SS_model_tab <- car::Anova(SS_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  SS_cld <- suppressMessages(
    suppressWarnings(
      left_join(SS_summ_sec, 
                multcomp::cld(
                  emmeans(SS_model, ~ SectionName, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(SectionName, Group))
      ))
  
   p <- SS_cld %>%
        ggplot(aes(SectionName, meanLive, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme
   
  } else {
     p <- SS_summ_sec %>%
        ggplot(aes(SectionName, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme 
  }
#
#
if(exists("SS_model_tab")){
  SS_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Section model results")
}

p

## Summary info
SS_sec_min <- SS_summ_sec %>% slice_min(meanLive, n = 1, with_ties = TRUE)
SS_sec_max <- SS_summ_sec %>% slice_max(meanLive, n = 1, with_ties = TRUE)
SS_sec_mean <- SS_summ_sec %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("SS_model_tab")){
  pValue <- car::Anova(All_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary:**
The mean number of live oysters surveyed in `r unique(SS_summ$Estuary)` ranged from `r round(SS_sec_min$meanLive,1)` oysters/m2 in `r SS_sec_min$SectionName` to `r round(SS_sec_max$meanLive,1)` oysters/m2 in `r SS_sec_max$SectionName` with an overall average of `r round(SS_sec_mean$mean,1)` +/- `r round(SS_sec_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among estuary sections `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\
```{r SS sections annual plot, echo = FALSE, fig.align='center'}
Section_Ann_summ %>%
  filter(Estuary == "SS") %>%
  ggplot(aes(Year, meanLive, group = SectionName))+
  geom_line(aes(color = SectionName), linewidth = 1.5)+
  geom_point(aes(color = SectionName), size = 3)+
  scale_x_discrete(expand = c(0.01,0.1))+
  scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
  scale_colour_viridis_d("Section")+
  ggtitle("Annual mean oysters/m2 per section")+
  basetheme + theme(axis.text.x = element_text(angle = 45))
```

### {-}

# St Pete Lab 

## Lake Worth {.tabset}

### Estuary 

```{r LW summary, echo = FALSE, fig.align='center', asis = TRUE}
#
# Filter to Estuary:
LW_summ <- Annual_summ %>% 
  filter(Estuary == "LW") %>%
  droplevels()

# Annual means table
LW_summ %>%
  ungroup() %>%
  dplyr::select(Year,
                `Mean` = meanLive,
                `SE` = seLive) %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Annual live oyster density")

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "LW") %>%
  mutate(Year = as.factor(Year)) %>% 
  group_by(Estuary, SectionName, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$Year) > 1) {
  set.seed(54321)
  LW_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ as.numeric(Year) + (1|SectionName), family = nbinom2, data = model_data))
  LW_model2 <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ Year + (1|SectionName), family = nbinom2, data = model_data))
  } else {
    rm(model_data)
    cat("Only one survey year is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("LW_model") && !is.null(LW_model)){
  LW_model_tab <- car::Anova(LW_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  LW_cld <- suppressMessages(
    suppressWarnings(
      left_join(LW_summ, 
                multcomp::cld(
                  emmeans(LW_model2, ~ Year, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(Year, Group))
      ))
  
   p <- LW_cld %>%
        ggplot(aes(Year, meanLive, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
   
  } else {
     p <- LW_summ %>%
        ggplot(aes(Year, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
  }
#
#
if(exists("LW_model_tab")){
  LW_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Annual model results")
}

p

## Summary info
LW_min <- LW_summ %>% group_by(Estuary) %>% slice_min(meanLive, n = 1, with_ties = TRUE)
LW_max <- LW_summ %>% group_by(Estuary) %>% slice_max(meanLive, n = 1, with_ties = TRUE)
LW_mean <- LW_summ %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("LW_model_tab")){
  pValue <- car::Anova(LW_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary**
The mean number of live oysters surveyed in `r unique(LW_summ$Estuary)` ranged from `r round(LW_min$meanLive,1)` oysters/m2 in `r LW_min$Year` to `r round(LW_max$meanLive,1)` oysters/m2 in `r LW_max$Year` with an overall average of `r round(LW_mean$mean,1)` +/- `r round(LW_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among years `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\

### Sections

```{r LW section summary, echo = FALSE, fig.align='center'}
#
# Filter to Estuary:
LW_summ_sec <- Section_summ %>% 
  filter(Estuary == "LW") %>%
  droplevels()

# Annual means table
LW_summ_sec %>%
  ungroup() %>%
  dplyr::select(`Section` = SectionName, 
                `Mean` = meanLive,
                `SE` = seLive) %>%
  #pivot_wider(
  #  names_from = SectionName,
  #  values_from = c(Mean, SE),
  #  names_glue = "{SectionName}_{.value}",
  #  names_vary = "slowest") %>% #Orders columns by SectionName
  gt() %>%
  #tab_spanner_delim(delim = "_") %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Average live oyster density") 

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "LW") %>%
  mutate(across(c(Year, SectionName, StationNumber), as.factor)) %>% 
  group_by(SectionName, StationNumber, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$SectionName) > 1) {
  set.seed(54321)
  LW_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ SectionName + (1|StationNumber), family = nbinom2, data = model_data))
} else {
  rm(model_data)
  cat("Only one estuary section is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("LW_model") && !is.null(LW_model)){
  LW_model_tab <- car::Anova(LW_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  LW_cld <- suppressMessages(
    suppressWarnings(
      left_join(LW_summ_sec, 
                multcomp::cld(
                  emmeans(LW_model, ~ SectionName, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(SectionName, Group))
      ))
  
   p <- LW_cld %>%
        ggplot(aes(SectionName, meanLive, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme
   
  } else {
     p <- LW_summ_sec %>%
        ggplot(aes(SectionName, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme 
  }
#
#
if(exists("LW_model_tab")){
  LW_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Section model results")
}

p

## Summary info
LW_sec_min <- LW_summ_sec %>% slice_min(meanLive, n = 1, with_ties = TRUE)
LW_sec_max <- LW_summ_sec %>% slice_max(meanLive, n = 1, with_ties = TRUE)
LW_sec_mean <- LW_summ_sec %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("LW_model_tab")){
  pValue <- car::Anova(All_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary:**
The mean number of live oysters surveyed in `r unique(LW_summ$Estuary)` ranged from `r round(LW_sec_min$meanLive,1)` oysters/m2 in `r LW_sec_min$SectionName` to `r round(LW_sec_max$meanLive,1)` oysters/m2 in `r LW_sec_max$SectionName` with an overall average of `r round(LW_sec_mean$mean,1)` +/- `r round(LW_sec_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among estuary sections `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\
```{r LW sections annual plot, echo = FALSE, fig.align='center'}
Section_Ann_summ %>%
  filter(Estuary == "LW") %>%
  ggplot(aes(Year, meanLive, group = SectionName))+
  geom_line(aes(color = SectionName), linewidth = 1.5)+
  geom_point(aes(color = SectionName), size = 3)+
  scale_x_discrete(expand = c(0.01,0.1))+
  scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
  scale_colour_viridis_d("Section")+
  ggtitle("Annual mean oysters/m2 per section")+
  basetheme + theme(axis.text.x = element_text(angle = 45))
```

### {-}

## Loxahatchee {.tabset}

### Estuary 

```{r LX summary, echo = FALSE, fig.align='center', asis = TRUE}
#
# Filter to Estuary:
LX_summ <- Annual_summ %>% 
  filter(Estuary == "LX") %>%
  droplevels()

# Annual means table
LX_summ %>%
  ungroup() %>%
  dplyr::select(Year,
                `Mean` = meanLive,
                `SE` = seLive) %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Annual live oyster density")

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "LX") %>%
  mutate(Year = as.factor(Year)) %>% 
  group_by(Estuary, SectionName, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$Year) > 1) {
  set.seed(54321)
  LX_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ as.numeric(Year) + (1|SectionName), family = nbinom2, data = model_data))
  LX_model2 <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ Year + (1|SectionName), family = nbinom2, data = model_data))
  } else {
    rm(model_data)
    cat("Only one survey year is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("LX_model") && !is.null(LX_model)){
  LX_model_tab <- car::Anova(LX_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  LX_cld <- suppressMessages(
    suppressWarnings(
      left_join(LX_summ, 
                multcomp::cld(
                  emmeans(LX_model2, ~ Year, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(Year, Group))
      ))
  
   p <- LX_cld %>%
        ggplot(aes(Year, meanLive, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
   
  } else {
     p <- LX_summ %>%
        ggplot(aes(Year, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
  }
#
#
if(exists("LX_model_tab")){
  LX_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Annual model results")
}

p

## Summary info
LX_min <- LX_summ %>% group_by(Estuary) %>% slice_min(meanLive, n = 1, with_ties = TRUE)
LX_max <- LX_summ %>% group_by(Estuary) %>% slice_max(meanLive, n = 1, with_ties = TRUE)
LX_mean <- LX_summ %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("LX_model_tab")){
  pValue <- car::Anova(LX_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary**
The mean number of live oysters surveyed in `r unique(LX_summ$Estuary)` ranged from `r round(LX_min$meanLive,1)` oysters/m2 in `r LX_min$Year` to `r round(LX_max$meanLive,1)` oysters/m2 in `r LX_max$Year` with an overall average of `r round(LX_mean$mean,1)` +/- `r round(LX_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among years `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\

### Sections

```{r LX section summary, echo = FALSE, fig.align='center'}
#
# Filter to Estuary:
LX_summ_sec <- Section_summ %>% 
  filter(Estuary == "LX") %>%
  droplevels()

# Annual means table
LX_summ_sec %>%
  ungroup() %>%
  dplyr::select(`Section` = SectionName, 
                `Mean` = meanLive,
                `SE` = seLive) %>%
  #pivot_wider(
  #  names_from = SectionName,
  #  values_from = c(Mean, SE),
  #  names_glue = "{SectionName}_{.value}",
  #  names_vary = "slowest") %>% #Orders columns by SectionName
  gt() %>%
  #tab_spanner_delim(delim = "_") %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Average live oyster density") 

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "LX") %>%
  mutate(across(c(Year, SectionName, StationNumber), as.factor)) %>% 
  group_by(SectionName, StationNumber, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$SectionName) > 1) {
  set.seed(54321)
  LX_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ SectionName + (1|StationNumber), family = nbinom2, data = model_data))
} else {
  rm(model_data)
  cat("Only one estuary section is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("LX_model") && !is.null(LX_model)){
  LX_model_tab <- car::Anova(LX_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  LX_cld <- suppressMessages(
    suppressWarnings(
      left_join(LX_summ_sec, 
                multcomp::cld(
                  emmeans(LX_model, ~ SectionName, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(SectionName, Group))
      ))
  
   p <- LX_cld %>%
        ggplot(aes(SectionName, meanLive, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme
   
  } else {
     p <- LX_summ_sec %>%
        ggplot(aes(SectionName, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme 
  }
#
#
if(exists("LX_model_tab")){
  LX_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Section model results")
}

p

## Summary info
LX_sec_min <- LX_summ_sec %>% slice_min(meanLive, n = 1, with_ties = TRUE)
LX_sec_max <- LX_summ_sec %>% slice_max(meanLive, n = 1, with_ties = TRUE)
LX_sec_mean <- LX_summ_sec %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("LX_model_tab")){
  pValue <- car::Anova(All_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary:**
The mean number of live oysters surveyed in `r unique(LX_summ$Estuary)` ranged from `r round(LX_sec_min$meanLive,1)` oysters/m2 in `r LX_sec_min$SectionName` to `r round(LX_sec_max$meanLive,1)` oysters/m2 in `r LX_sec_max$SectionName` with an overall average of `r round(LX_sec_mean$mean,1)` +/- `r round(LX_sec_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among estuary sections `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\
```{r LX sections annual plot, echo = FALSE, fig.align='center'}
Section_Ann_summ %>%
  filter(Estuary == "LX") %>%
  ggplot(aes(Year, meanLive, group = SectionName))+
  geom_line(aes(color = SectionName), linewidth = 1.5)+
  geom_point(aes(color = SectionName), size = 3)+
  scale_x_discrete(expand = c(0.01,0.1))+
  scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
  scale_colour_viridis_d("Section")+
  ggtitle("Annual mean oysters/m2 per section")+
  basetheme + theme(axis.text.x = element_text(angle = 45))
```

### {-}

## St. Lucie {.tabset}

### Estuary 

```{r SL summary, echo = FALSE, fig.align='center', asis = TRUE}
#
# Filter to Estuary:
SL_summ <- Annual_summ %>% 
  filter(Estuary == "SL") %>%
  droplevels()

# Annual means table
SL_summ %>%
  ungroup() %>%
  dplyr::select(Year,
                `Mean` = meanLive,
                `SE` = seLive) %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Annual live oyster density")

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "SL") %>%
  mutate(Year = as.factor(Year)) %>% 
  group_by(Estuary, SectionName, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$Year) > 1) {
  set.seed(54321)
  SL_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ as.numeric(Year) + (1|SectionName), family = nbinom2, data = model_data))
  SL_model2 <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ Year + (1|SectionName), family = nbinom2, data = model_data))
  } else {
    rm(model_data)
    cat("Only one survey year is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("SL_model") && !is.null(SL_model)){
  SL_model_tab <- car::Anova(SL_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  SL_cld <- suppressMessages(
    suppressWarnings(
      left_join(SL_summ, 
                multcomp::cld(
                  emmeans(SL_model2, ~ Year, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(Year, Group))
      ))
  
   p <- SL_cld %>%
        ggplot(aes(Year, meanLive, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
   
  } else {
     p <- SL_summ %>%
        ggplot(aes(Year, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
  }
#
#
if(exists("SL_model_tab")){
  SL_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Annual model results")
}

p

## Summary info
SL_min <- SL_summ %>% group_by(Estuary) %>% slice_min(meanLive, n = 1, with_ties = TRUE)
SL_max <- SL_summ %>% group_by(Estuary) %>% slice_max(meanLive, n = 1, with_ties = TRUE)
SL_mean <- SL_summ %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("SL_model_tab")){
  pValue <- car::Anova(SL_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary**
The mean number of live oysters surveyed in `r unique(SL_summ$Estuary)` ranged from `r round(SL_min$meanLive,1)` oysters/m2 in `r SL_min$Year` to `r round(SL_max$meanLive,1)` oysters/m2 in `r SL_max$Year` with an overall average of `r round(SL_mean$mean,1)` +/- `r round(SL_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among years `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\

### Sections

```{r SL section summary, echo = FALSE, fig.align='center'}
#
# Filter to Estuary:
SL_summ_sec <- Section_summ %>% 
  filter(Estuary == "SL") %>%
  droplevels()

# Annual means table
SL_summ_sec %>%
  ungroup() %>%
  dplyr::select(`Section` = SectionName, 
                `Mean` = meanLive,
                `SE` = seLive) %>%
  #pivot_wider(
  #  names_from = SectionName,
  #  values_from = c(Mean, SE),
  #  names_glue = "{SectionName}_{.value}",
  #  names_vary = "slowest") %>% #Orders columns by SectionName
  gt() %>%
  #tab_spanner_delim(delim = "_") %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Average live oyster density") 

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "SL") %>%
  mutate(across(c(Year, SectionName, StationNumber), as.factor)) %>% 
  group_by(SectionName, StationNumber, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$SectionName) > 1) {
  set.seed(54321)
  SL_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ SectionName + (1|StationNumber), family = nbinom2, data = model_data))
} else {
  rm(model_data)
  cat("Only one estuary section is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("SL_model") && !is.null(SL_model)){
  SL_model_tab <- car::Anova(SL_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  SL_cld <- suppressMessages(
    suppressWarnings(
      left_join(SL_summ_sec, 
                multcomp::cld(
                  emmeans(SL_model, ~ SectionName, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(SectionName, Group))
      ))
  
   p <- SL_cld %>%
        ggplot(aes(SectionName, meanLive, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme
   
  } else {
     p <- SL_summ_sec %>%
        ggplot(aes(SectionName, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme 
  }
#
#
if(exists("SL_model_tab")){
  SL_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Section model results")
}

p

## Summary info
SL_sec_min <- SL_summ_sec %>% slice_min(meanLive, n = 1, with_ties = TRUE)
SL_sec_max <- SL_summ_sec %>% slice_max(meanLive, n = 1, with_ties = TRUE)
SL_sec_mean <- SL_summ_sec %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("SL_model_tab")){
  pValue <- car::Anova(All_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary:**
The mean number of live oysters surveyed in `r unique(SL_summ$Estuary)` ranged from `r round(SL_sec_min$meanLive,1)` oysters/m2 in `r SL_sec_min$SectionName` to `r round(SL_sec_max$meanLive,1)` oysters/m2 in `r SL_sec_max$SectionName` with an overall average of `r round(SL_sec_mean$mean,1)` +/- `r round(SL_sec_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among estuary sections `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\
```{r SL sections annual plot, echo = FALSE, fig.align='center'}
Section_Ann_summ %>%
  filter(Estuary == "SL") %>%
  ggplot(aes(Year, meanLive, group = SectionName))+
  geom_line(aes(color = SectionName), linewidth = 1.5)+
  geom_point(aes(color = SectionName), size = 3)+
  scale_x_discrete(expand = c(0.01,0.1))+
  scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
  scale_colour_viridis_d("Section")+
  ggtitle("Annual mean oysters/m2 per section")+
  basetheme + theme(axis.text.x = element_text(angle = 45))
```

### {-}

## Caloosahatchee {.tabset}

### Estuary 

```{r CR summary, echo = FALSE, fig.align='center', asis = TRUE}
#
# Filter to Estuary:
CR_summ <- Annual_summ %>% 
  filter(Estuary == "CR") %>%
  droplevels()

# Annual means table
CR_summ %>%
  ungroup() %>%
  dplyr::select(Year,
                `Mean` = meanLive,
                `SE` = seLive) %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Annual live oyster density")

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "CR") %>%
  mutate(Year = as.factor(Year)) %>% 
  group_by(Estuary, SectionName, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$Year) > 1) {
  set.seed(54321)
  CR_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ as.numeric(Year) + (1|SectionName), family = nbinom2, data = model_data))
  CR_model2 <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ Year + (1|SectionName), family = nbinom2, data = model_data))
  } else {
    rm(model_data)
    cat("Only one survey year is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("CR_model") && !is.null(CR_model)){
  CR_model_tab <- car::Anova(CR_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  CR_cld <- suppressMessages(
    suppressWarnings(
      left_join(CR_summ, 
                multcomp::cld(
                  emmeans(CR_model2, ~ Year, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(Year, Group))
      ))
  
   p <- CR_cld %>%
        ggplot(aes(Year, meanLive, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
   
  } else {
     p <- CR_summ %>%
        ggplot(aes(Year, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
  }
#
#
if(exists("CR_model_tab")){
  CR_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Annual model results")
}

p

## Summary info
CR_min <- CR_summ %>% group_by(Estuary) %>% slice_min(meanLive, n = 1, with_ties = TRUE)
CR_max <- CR_summ %>% group_by(Estuary) %>% slice_max(meanLive, n = 1, with_ties = TRUE)
CR_mean <- CR_summ %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("CR_model_tab")){
  pValue <- car::Anova(CR_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary**
The mean number of live oysters surveyed in `r unique(CR_summ$Estuary)` ranged from `r round(CR_min$meanLive,1)` oysters/m2 in `r CR_min$Year` to `r round(CR_max$meanLive,1)` oysters/m2 in `r CR_max$Year` with an overall average of `r round(CR_mean$mean,1)` +/- `r round(CR_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among years `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\

### Sections

```{r CR section summary, echo = FALSE, fig.align='center'}
#
# Filter to Estuary:
CR_summ_sec <- Section_summ %>% 
  filter(Estuary == "CR") %>%
  droplevels()

# Annual means table
CR_summ_sec %>%
  ungroup() %>%
  dplyr::select(`Section` = SectionName, 
                `Mean` = meanLive,
                `SE` = seLive) %>%
  #pivot_wider(
  #  names_from = SectionName,
  #  values_from = c(Mean, SE),
  #  names_glue = "{SectionName}_{.value}",
  #  names_vary = "slowest") %>% #Orders columns by SectionName
  gt() %>%
  #tab_spanner_delim(delim = "_") %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Average live oyster density") 

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "CR") %>%
  mutate(across(c(Year, SectionName, StationNumber), as.factor)) %>% 
  group_by(SectionName, StationNumber, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$SectionName) > 1) {
  set.seed(54321)
  CR_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ SectionName + (1|StationNumber), family = nbinom2, data = model_data))
} else {
  rm(model_data)
  cat("Only one estuary section is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("CR_model") && !is.null(CR_model)){
  CR_model_tab <- car::Anova(CR_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  CR_cld <- suppressMessages(
    suppressWarnings(
      left_join(CR_summ_sec, 
                multcomp::cld(
                  emmeans(CR_model, ~ SectionName, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(SectionName, Group))
      ))
  
   p <- CR_cld %>%
        ggplot(aes(SectionName, meanLive, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme
   
  } else {
     p <- CR_summ_sec %>%
        ggplot(aes(SectionName, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme 
  }
#
#
if(exists("CR_model_tab")){
  CR_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Section model results")
}

p

## Summary info
CR_sec_min <- CR_summ_sec %>% slice_min(meanLive, n = 1, with_ties = TRUE)
CR_sec_max <- CR_summ_sec %>% slice_max(meanLive, n = 1, with_ties = TRUE)
CR_sec_mean <- CR_summ_sec %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("CR_model_tab")){
  pValue <- car::Anova(All_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary:**
The mean number of live oysters surveyed in `r unique(CR_summ$Estuary)` ranged from `r round(CR_sec_min$meanLive,1)` oysters/m2 in `r CR_sec_min$SectionName` to `r round(CR_sec_max$meanLive,1)` oysters/m2 in `r CR_sec_max$SectionName` with an overall average of `r round(CR_sec_mean$mean,1)` +/- `r round(CR_sec_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among estuary sections `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\
```{r CR sections annual plot, echo = FALSE, fig.align='center'}
Section_Ann_summ %>%
  filter(Estuary == "CR") %>%
  ggplot(aes(Year, meanLive, group = SectionName))+
  geom_line(aes(color = SectionName), linewidth = 1.5)+
  geom_point(aes(color = SectionName), size = 3)+
  scale_x_discrete(expand = c(0.01,0.1))+
  scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
  scale_colour_viridis_d("Section")+
  ggtitle("Annual mean oysters/m2 per section")+
  basetheme + theme(axis.text.x = element_text(angle = 45))
```

### {-}

## Tampa Bay {.tabset}

### Estuary 

```{r TB summary, echo = FALSE, fig.align='center', asis = TRUE}
#
# Filter to Estuary:
TB_summ <- Annual_summ %>% 
  filter(Estuary == "TB") %>%
  droplevels()

# Annual means table
TB_summ %>%
  ungroup() %>%
  dplyr::select(Year,
                `Mean` = meanLive,
                `SE` = seLive) %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Annual live oyster density")

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "TB") %>%
  mutate(Year = as.factor(Year)) %>% 
  group_by(Estuary, SectionName, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$Year) > 1) {
  set.seed(54321)
  TB_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ as.numeric(Year) + (1|SectionName), family = nbinom2, data = model_data))
  TB_model2 <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ Year + (1|SectionName), family = nbinom2, data = model_data))
  } else {
    rm(model_data)
    cat("Only one survey year is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("TB_model") && !is.null(TB_model)){
  TB_model_tab <- car::Anova(TB_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  TB_cld <- suppressMessages(
    suppressWarnings(
      left_join(TB_summ, 
                multcomp::cld(
                  emmeans(TB_model2, ~ Year, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(Year, Group))
      ))
  
   p <- TB_cld %>%
        ggplot(aes(Year, meanLive, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
   
  } else {
     p <- TB_summ %>%
        ggplot(aes(Year, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
  }
#
#
if(exists("TB_model_tab")){
  TB_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Annual model results")
}

p

## Summary info
TB_min <- TB_summ %>% group_by(Estuary) %>% slice_min(meanLive, n = 1, with_ties = TRUE)
TB_max <- TB_summ %>% group_by(Estuary) %>% slice_max(meanLive, n = 1, with_ties = TRUE)
TB_mean <- TB_summ %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("TB_model_tab")){
  pValue <- car::Anova(TB_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary**
The mean number of live oysters surveyed in `r unique(TB_summ$Estuary)` ranged from `r round(TB_min$meanLive,1)` oysters/m2 in `r TB_min$Year` to `r round(TB_max$meanLive,1)` oysters/m2 in `r TB_max$Year` with an overall average of `r round(TB_mean$mean,1)` +/- `r round(TB_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among years `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\

### Sections

```{r TB section summary, echo = FALSE, fig.align='center'}
#
# Filter to Estuary:
TB_summ_sec <- Section_summ %>% 
  filter(Estuary == "TB") %>%
  droplevels()

# Annual means table
TB_summ_sec %>%
  ungroup() %>%
  dplyr::select(`Section` = SectionName, 
                `Mean` = meanLive,
                `SE` = seLive) %>%
  #pivot_wider(
  #  names_from = SectionName,
  #  values_from = c(Mean, SE),
  #  names_glue = "{SectionName}_{.value}",
  #  names_vary = "slowest") %>% #Orders columns by SectionName
  gt() %>%
  #tab_spanner_delim(delim = "_") %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Average live oyster density") 

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "TB") %>%
  mutate(across(c(Year, SectionName, StationNumber), as.factor)) %>% 
  group_by(SectionName, StationNumber, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$SectionName) > 1) {
  set.seed(54321)
  TB_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ SectionName + (1|StationNumber), family = nbinom2, data = model_data))
} else {
  rm(model_data)
  cat("Only one estuary section is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("TB_model") && !is.null(TB_model)){
  TB_model_tab <- car::Anova(TB_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  TB_cld <- suppressMessages(
    suppressWarnings(
      left_join(TB_summ_sec, 
                multcomp::cld(
                  emmeans(TB_model, ~ SectionName, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(SectionName, Group))
      ))
  
   p <- TB_cld %>%
        ggplot(aes(SectionName, meanLive, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme
   
  } else {
     p <- TB_summ_sec %>%
        ggplot(aes(SectionName, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme 
  }
#
#
if(exists("TB_model_tab")){
  TB_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Section model results")
}

p

## Summary info
TB_sec_min <- TB_summ_sec %>% slice_min(meanLive, n = 1, with_ties = TRUE)
TB_sec_max <- TB_summ_sec %>% slice_max(meanLive, n = 1, with_ties = TRUE)
TB_sec_mean <- TB_summ_sec %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("TB_model_tab")){
  pValue <- car::Anova(All_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary:**
The mean number of live oysters surveyed in `r unique(TB_summ$Estuary)` ranged from `r round(TB_sec_min$meanLive,1)` oysters/m2 in `r TB_sec_min$SectionName` to `r round(TB_sec_max$meanLive,1)` oysters/m2 in `r TB_sec_max$SectionName` with an overall average of `r round(TB_sec_mean$mean,1)` +/- `r round(TB_sec_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among estuary sections `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\
```{r TB sections annual plot, echo = FALSE, fig.align='center'}
Section_Ann_summ %>%
  filter(Estuary == "TB") %>%
  ggplot(aes(Year, meanLive, group = SectionName))+
  geom_line(aes(color = SectionName), linewidth = 1.5)+
  geom_point(aes(color = SectionName), size = 3)+
  scale_x_discrete(expand = c(0.01,0.1))+
  scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
  scale_colour_viridis_d("Section")+
  ggtitle("Annual mean oysters/m2 per section")+
  basetheme + theme(axis.text.x = element_text(angle = 45))
```

### {-}

## Biscayne Bay {.tabset}

### Estuary 

```{r BB summary, echo = FALSE, fig.align='center', asis = TRUE}
#
# Filter to Estuary:
BB_summ <- Annual_summ %>% 
  filter(Estuary == "BB") %>%
  droplevels()

# Annual means table
BB_summ %>%
  ungroup() %>%
  dplyr::select(Year,
                `Mean` = meanLive,
                `SE` = seLive) %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Annual live oyster density")

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "BB") %>%
  mutate(Year = as.factor(Year)) %>% 
  group_by(Estuary, SectionName, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$Year) > 1) {
  set.seed(54321)
  BB_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ as.numeric(Year) + (1|SectionName), family = nbinom2, data = model_data))
  BB_model2 <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ Year + (1|SectionName), family = nbinom2, data = model_data))
  } else {
    rm(model_data)
    cat("Only one survey year is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("BB_model") && !is.null(BB_model)){
  BB_model_tab <- car::Anova(BB_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  BB_cld <- suppressMessages(
    suppressWarnings(
      left_join(BB_summ, 
                multcomp::cld(
                  emmeans(BB_model2, ~ Year, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(Year, Group))
      ))
  
   p <- BB_cld %>%
        ggplot(aes(Year, meanLive, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
   
  } else {
     p <- BB_summ %>%
        ggplot(aes(Year, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
  }
#
#
if(exists("BB_model_tab")){
  BB_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Annual model results")
}

p

## Summary info
BB_min <- BB_summ %>% group_by(Estuary) %>% slice_min(meanLive, n = 1, with_ties = TRUE)
BB_max <- BB_summ %>% group_by(Estuary) %>% slice_max(meanLive, n = 1, with_ties = TRUE)
BB_mean <- BB_summ %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("BB_model_tab")){
  pValue <- car::Anova(BB_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary**
The mean number of live oysters surveyed in `r unique(BB_summ$Estuary)` ranged from `r round(BB_min$meanLive,1)` oysters/m2 in `r BB_min$Year` to `r round(BB_max$meanLive,1)` oysters/m2 in `r BB_max$Year` with an overall average of `r round(BB_mean$mean,1)` +/- `r round(BB_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5 && !is.na(pValue$p.value[2])){paste("varied significantly")} else {paste("did not vary significantly")}` among years `r if(!is.null(pValue) && pValue$p.value[2] < 0.001 && !is.na(pValue$p.value[2])){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\

### Sections

```{r BB section summary, echo = FALSE, fig.align='center'}
#
# Filter to Estuary:
BB_summ_sec <- Section_summ %>% 
  filter(Estuary == "BB") %>%
  droplevels()

# Annual means table
BB_summ_sec %>%
  ungroup() %>%
  dplyr::select(`Section` = SectionName, 
                `Mean` = meanLive,
                `SE` = seLive) %>%
  #pivot_wider(
  #  names_from = SectionName,
  #  values_from = c(Mean, SE),
  #  names_glue = "{SectionName}_{.value}",
  #  names_vary = "slowest") %>% #Orders columns by SectionName
  gt() %>%
  #tab_spanner_delim(delim = "_") %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Average live oyster density") 

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "BB") %>%
  mutate(across(c(Year, SectionName, StationNumber), as.factor)) %>% 
  group_by(SectionName, StationNumber, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$SectionName) > 1) {
  set.seed(54321)
  BB_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ SectionName + (1|StationNumber), family = nbinom2, data = model_data))
} else {
  rm(model_data)
  cat("Only one estuary section is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("BB_model") && !is.null(BB_model)){
  BB_model_tab <- car::Anova(BB_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  BB_cld <- BB_summ_sec
  
   p <- BB_cld %>%
        ggplot(aes(SectionName, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme
   
  } else {
     p <- BB_summ_sec %>%
        ggplot(aes(SectionName, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme 
  }
#
#
if(exists("BB_model_tab")){
  BB_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Section model results")
}

p

## Summary info
BB_sec_min <- BB_summ_sec %>% slice_min(meanLive, n = 1, with_ties = TRUE)
BB_sec_max <- BB_summ_sec %>% slice_max(meanLive, n = 1, with_ties = TRUE)
BB_sec_mean <- BB_summ_sec %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("BB_model_tab")){
  pValue <- car::Anova(All_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary:**
The mean number of live oysters surveyed in `r unique(BB_summ$Estuary)` ranged from `r round(BB_sec_min$meanLive,1)` oysters/m2 in `r BB_sec_min$SectionName` to `r round(BB_sec_max$meanLive,1)` oysters/m2 in `r BB_sec_max$SectionName` with an overall average of `r round(BB_sec_mean$mean,1)` +/- `r round(BB_sec_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among estuary sections `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\
```{r BB sections annual plot, echo = FALSE, fig.align='center'}
Section_Ann_summ %>%
  filter(Estuary == "BB") %>%
  ggplot(aes(Year, meanLive, group = SectionName))+
  geom_line(aes(color = SectionName), linewidth = 1.5)+
  geom_point(aes(color = SectionName), size = 3)+
  scale_x_discrete(expand = c(0.01,0.1))+
  scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
  scale_colour_viridis_d("Section")+
  ggtitle("Annual mean oysters/m2 per section")+
  basetheme + theme(axis.text.x = element_text(angle = 45))
```

### {-}

## Mosquito Lagoon {.tabset}

### Estuary 

```{r ML summary, echo = FALSE, fig.align='center', asis = TRUE}
#
# Filter to Estuary:
ML_summ <- Annual_summ %>% 
  filter(Estuary == "ML") %>%
  droplevels()

# Annual means table
ML_summ %>%
  ungroup() %>%
  dplyr::select(Year,
                `Mean` = meanLive,
                `SE` = seLive) %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Annual live oyster density")

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "ML") %>%
  mutate(Year = as.factor(Year)) %>% 
  group_by(Estuary, SectionName, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$Year) > 1) {
  set.seed(54321)
  ML_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ as.numeric(Year) + (1|SectionName), family = nbinom2, data = model_data))
  ML_model2 <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ Year + (1|SectionName), family = nbinom2, data = model_data))
  } else {
    rm(model_data)
    cat("Only one survey year is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("ML_model") && !is.null(ML_model)){
  ML_model_tab <- car::Anova(ML_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  ML_cld <- suppressMessages(
    suppressWarnings(
      left_join(ML_summ, 
                multcomp::cld(
                  emmeans(ML_model2, ~ Year, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(Year, Group))
      ))
  
   p <- ML_cld %>%
        ggplot(aes(Year, meanLive, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
   
  } else {
     p <- ML_summ %>%
        ggplot(aes(Year, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
  }
#
#
if(exists("ML_model_tab")){
  ML_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Annual model results")
}

p

## Summary info
ML_min <- ML_summ %>% group_by(Estuary) %>% slice_min(meanLive, n = 1, with_ties = TRUE)
ML_max <- ML_summ %>% group_by(Estuary) %>% slice_max(meanLive, n = 1, with_ties = TRUE)
ML_mean <- ML_summ %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("ML_model_tab")){
  pValue <- car::Anova(ML_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary**
The mean number of live oysters surveyed in `r unique(ML_summ$Estuary)` ranged from `r round(ML_min$meanLive,1)` oysters/m2 in `r ML_min$Year` to `r round(ML_max$meanLive,1)` oysters/m2 in `r ML_max$Year` with an overall average of `r round(ML_mean$mean,1)` +/- `r round(ML_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among years `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\

### Sections

```{r ML section summary, echo = FALSE, fig.align='center'}
#
# Filter to Estuary:
ML_summ_sec <- Section_summ %>% 
  filter(Estuary == "ML") %>%
  droplevels()

# Annual means table
ML_summ_sec %>%
  ungroup() %>%
  dplyr::select(`Section` = SectionName, 
                `Mean` = meanLive,
                `SE` = seLive) %>%
  #pivot_wider(
  #  names_from = SectionName,
  #  values_from = c(Mean, SE),
  #  names_glue = "{SectionName}_{.value}",
  #  names_vary = "slowest") %>% #Orders columns by SectionName
  gt() %>%
  #tab_spanner_delim(delim = "_") %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Average live oyster density") 

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "ML") %>%
  mutate(across(c(Year, SectionName, StationNumber), as.factor)) %>% 
  group_by(SectionName, StationNumber, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$SectionName) > 1) {
  set.seed(54321)
  ML_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ SectionName + (1|StationNumber), family = nbinom2, data = model_data))
} else {
  rm(model_data)
  cat("Only one estuary section is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("ML_model") && !is.null(ML_model)){
  ML_model_tab <- car::Anova(ML_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  ML_cld <-ML_summ_sec
  
   p <- ML_cld %>%
        ggplot(aes(SectionName, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme
   
  } else {
     p <- ML_summ_sec %>%
       ggplot(aes(SectionName, meanLive))+
       geom_bar(stat = "identity")+
       geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
       scale_x_discrete(expand = c(0.05,0.1))+
       scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
       basetheme 
  }
#
#
if(exists("ML_model_tab")){
  ML_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Section model results")
}

p

## Summary info
ML_sec_min <- ML_summ_sec %>% slice_min(meanLive, n = 1, with_ties = TRUE)
ML_sec_max <- ML_summ_sec %>% slice_max(meanLive, n = 1, with_ties = TRUE)
ML_sec_mean <- ML_summ_sec %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("ML_model_tab")){
  pValue <- car::Anova(All_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary:**
The mean number of live oysters surveyed in `r unique(ML_summ$Estuary)` ranged from `r round(ML_sec_min$meanLive,1)` oysters/m2 in `r ML_sec_min$SectionName` to `r round(ML_sec_max$meanLive,1)` oysters/m2 in `r ML_sec_max$SectionName` with an overall average of `r round(ML_sec_mean$mean,1)` +/- `r round(ML_sec_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among estuary sections `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\
```{r ML sections annual plot, echo = FALSE, fig.align='center'}
Section_Ann_summ %>%
  filter(Estuary == "ML") %>%
  ggplot(aes(Year, meanLive, group = SectionName))+
  geom_line(aes(color = SectionName), linewidth = 1.5)+
  geom_point(aes(color = SectionName), size = 3)+
  scale_x_discrete(expand = c(0.01,0.1))+
  scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
  scale_colour_viridis_d("Section")+
  ggtitle("Annual mean oysters/m2 per section")+
  basetheme + theme(axis.text.x = element_text(angle = 45))
```

### {-}

## Sebastian River {.tabset}

### Estuary 

```{r SR summary, echo = FALSE, fig.align='center', asis = TRUE}
#
# Filter to Estuary:
SR_summ <- Annual_summ %>% 
  filter(Estuary == "SR") %>%
  droplevels()

# Annual means table
SR_summ %>%
  ungroup() %>%
  dplyr::select(Year,
                `Mean` = meanLive,
                `SE` = seLive) %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Annual live oyster density")

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "SR") %>%
  mutate(Year = as.factor(Year)) %>% 
  group_by(Estuary, SectionName, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$Year) > 1) {
  set.seed(54321)
  SR_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ as.numeric(Year) + (1|SectionName), family = nbinom2, data = model_data))
  SR_model2 <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ Year + (1|SectionName), family = nbinom2, data = model_data))
  } else {
    rm(model_data)
    cat("Only one survey year is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("SR_model") && !is.null(SR_model)){
  SR_model_tab <- car::Anova(SR_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  SR_cld <- suppressMessages(
    suppressWarnings(
      left_join(SR_summ, 
                multcomp::cld(
                  emmeans(SR_model2, ~ Year, type = "response"),
                  Letters = letters, adjust = "sidak") %>%
                  as.data.frame() %>%
                  rename(Group = .group) %>%
                  mutate(Group = stringr::str_trim(Group)) %>%
                  dplyr::select(Year, Group))
      ))
  
   p <- SR_cld %>%
        ggplot(aes(Year, meanLive, fill = Group))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
   
  } else {
     p <- SR_summ %>%
        ggplot(aes(Year, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme + 
        theme(axis.text.x = element_text(angle = 45))
  }
#
#
if(exists("SR_model_tab")){
  SR_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Annual model results")
}

p

## Summary info
SR_min <- SR_summ %>% group_by(Estuary) %>% slice_min(meanLive, n = 1, with_ties = TRUE)
SR_max <- SR_summ %>% group_by(Estuary) %>% slice_max(meanLive, n = 1, with_ties = TRUE)
SR_mean <- SR_summ %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("SR_model_tab")){
  pValue <- car::Anova(SR_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary**
The mean number of live oysters surveyed in `r unique(SR_summ$Estuary)` ranged from `r round(SR_min$meanLive,1)` oysters/m2 in `r SR_min$Year` to `r round(SR_max$meanLive,1)` oysters/m2 in `r SR_max$Year` with an overall average of `r round(SR_mean$mean,1)` +/- `r round(SR_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among years `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\

### Sections

```{r SR section summary, echo = FALSE, fig.align='center'}
#
# Filter to Estuary:
SR_summ_sec <- Section_summ %>% 
  filter(Estuary == "SR") %>%
  droplevels()

# Annual means table
SR_summ_sec %>%
  ungroup() %>%
  dplyr::select(`Section` = SectionName, 
                `Mean` = meanLive,
                `SE` = seLive) %>%
  #pivot_wider(
  #  names_from = SectionName,
  #  values_from = c(Mean, SE),
  #  names_glue = "{SectionName}_{.value}",
  #  names_vary = "slowest") %>% #Orders columns by SectionName
  gt() %>%
  #tab_spanner_delim(delim = "_") %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Average live oyster density") 

# Annual means comps
model_data <- Quads_df %>% 
  filter(Estuary == "SR") %>%
  mutate(across(c(Year, SectionName, StationNumber), as.factor)) %>% 
  group_by(SectionName, StationNumber, Year) %>%
  summarise(MeanLive = mean(TotalLive, na.rm =T),
            .groups = "drop") %>%
  droplevels()
#
if (dplyr::n_distinct(model_data$SectionName) > 1) {
  set.seed(54321)
  SR_model <- suppressWarnings(glmmTMB::glmmTMB(MeanLive ~ SectionName + (1|StationNumber), family = nbinom2, data = model_data))
} else {
  rm(model_data)
  cat("Only one estuary section is available. Model fitting was skipped.\n\n")
}
#
# Model output
if(exists("SR_model") && !is.null(SR_model)){
  SR_model_tab <- car::Anova(SR_model, type = 3) %>%
    broom::tidy() %>% 
    as.data.frame() %>%
    mutate(statistic = round(statistic, 3),
           p.value = round(p.value, 3))
  SR_cld <- SR_summ_sec
  
   p <- SR_cld %>%
        ggplot(aes(SectionName, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        scale_fill_viridis_d()+
        basetheme
   
  } else {
     p <- SR_summ_sec %>%
        ggplot(aes(SectionName, meanLive))+
        geom_bar(stat = "identity")+
        geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
        scale_x_discrete(expand = c(0.05,0.1))+
        scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
        basetheme 
  }
#
#
if(exists("SR_model_tab")){
  SR_model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Section model results")
}

p

## Summary info
SR_sec_min <- SR_summ_sec %>% slice_min(meanLive, n = 1, with_ties = TRUE)
SR_sec_max <- SR_summ_sec %>% slice_max(meanLive, n = 1, with_ties = TRUE)
SR_sec_mean <- SR_summ_sec %>% ungroup() %>% summarise(mean = mean(meanLive, na.rm = T),
                                               sd = sd(meanLive, na.rm = T))
if(exists("SR_model_tab")){
  pValue <- car::Anova(All_model, type = 3) %>%
     broom::tidy() %>% 
     as.data.frame()
} else {
  pValue <- NULL
}
#
#
```
\
\
**Summary:**
The mean number of live oysters surveyed in `r unique(SR_summ$Estuary)` ranged from `r round(SR_sec_min$meanLive,1)` oysters/m2 in `r SR_sec_min$SectionName` to `r round(SR_sec_max$meanLive,1)` oysters/m2 in `r SR_sec_max$SectionName` with an overall average of `r round(SR_sec_mean$mean,1)` +/- `r round(SR_sec_mean$sd, 1)` oysters/m2. Mean live oyster density `r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` among estuary sections `r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\
```{r SR sections annual plot, echo = FALSE, fig.align='center'}
Section_Ann_summ %>%
  filter(Estuary == "SR") %>%
  ggplot(aes(Year, meanLive, group = SectionName))+
  geom_line(aes(color = SectionName), linewidth = 1.5)+
  geom_point(aes(color = SectionName), size = 3)+
  scale_x_discrete(expand = c(0.01,0.1))+
  scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
  scale_colour_viridis_d("Section")+
  ggtitle("Annual mean oysters/m2 per section")+
  basetheme + theme(axis.text.x = element_text(angle = 45))
```

### {-}
