---
title: "Survey data summary"
author: "EWilliams"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
#
# Set data type working with (based on database coding) and initials 
Data_type <- c("SRVY")
Initials <- c("ELW")
#
#
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
#Load packages, install as needed
#if (!require("remotes")) install.packages("remotes") pacman::p_unlock()
if (!require("pacman")) {install.packages("pacman")}
pacman::p_load(plyr, tidyverse, glue, purrr, #Df manipulation, 
               ggpubr, scales, lemon, ggnewscale, gt, #ploting, tables
               rstatix, broom, #Summary stats
               zoo, lubridate, forecast, #Dates and times
               readxl, #Reading excel files
               car, emmeans, multcomp, #Basic analyses
               lmPerm, stats, 
               glmmTMB, AICcmodavg, DHARMa, performance, modelsummary,
               install = TRUE)

```

```{r Formatting, include=FALSE}
#
# Establish consistent formatting for plots:
basetheme <- theme_bw()+
        # Set axis title and text parameters
  theme(axis.title = element_text(size = 14, face = "bold", color = "black", family = "serif"), 
        axis.text.x = element_text(size = 13, margin = margin(t=0.25, l=0.5, r=0.25, b=0.15, unit = "cm"), family = "serif"),
        axis.text.y = element_text(size = 13, margin = margin(t=0.25, l=0.25, r=0.1, b=0, unit = "cm"), family = "serif"),
        # Remove grid lines and box around plot
        panel.grid = element_blank(), 
        panel.border = element_blank(), 
        # Modify axes
        axis.line = element_line(color = "black"),
        axis.ticks.length = unit(-0.15, "cm"))
#
# Uniform scaling
adaptive_discrete_breaks <- function(categories) {
  n_breaks <- length(categories)
  if (n_breaks >= 12) {
    # Keep every 2nd category label (displays 10+ labels)
    return(categories[seq(1, n_breaks, by = 4)]) 
  } else if (n_breaks >= 9) {
    # Keep every 2nd category label (displays 6+ labels)
    return(categories[seq(1, n_breaks, by = 3)]) 
  } else if (n_breaks >= 6) {
    # Keep every 2nd break to cut 12 down to 6
    return(categories[seq(1, n_breaks, by = 2)]) 
  } else {
    # Less than 12 breaks: return ALL unique categories natively
    return(categories)
  }
}
adaptive_breaks <- function(limits) {
  #  Get the default neat breaks
  default_breaks <- scales::breaks_pretty(n = 12)(limits)
  n_breaks <- length(default_breaks)
  # Apply conditional filtering rules
  if (n_breaks >= 12) {
    # Keep every 2nd break to cut 20 down to 10
    return(default_breaks[seq(1, n_breaks, by = 4)]) 
  } else if (n_breaks >= 9) {
    # Keep every 2nd break to cut 12 down to 6
    return(default_breaks[seq(1, n_breaks, by = 3)]) 
  } else if (n_breaks >= 6) {
    # Keep every 2nd break to cut 12 down to 6
    return(default_breaks[seq(1, n_breaks, by = 2)]) 
  }else {
    # If less than 7 breaks (or between 7 and 11), use all defaults
    return(default_breaks)
  }
}
XYscales_dc <- list(scale_x_discrete(expand = expansion(mult = c(0, 0)), breaks = adaptive_discrete_breaks),
                   scale_y_continuous(expand = expansion(mult = c(0, 0)), breaks = adaptive_breaks))
XYscales_cc <- list(scale_x_continuous(expand = expansion(mult = c(0, 0)), breaks = adaptive_breaks),
                   scale_y_continuous(expand = expansion(mult = c(0, 0)), breaks = adaptive_breaks))
#
#
```

```{r Load data files, include=FALSE}

## Fixed Locations
FLID_raw <- read_excel("../Data/Srvy_data_clean_ELW.xlsx", sheet = "FLIDs", 
                       skip = 0, col_names = TRUE,  
                       na = c("", "NULL", " ", "NAN", "na"), trim_ws = TRUE, 
                       .name_repair = "unique") 
#
## Survey
Quads_raw <- read_excel("../Data/Srvy_data_clean_ELW.xlsx", sheet = "Quadrats", 
                       skip = 0, col_names = TRUE,  
                       na = c("", "NULL", " ", "NAN", "na"), trim_ws = TRUE, 
                       .name_repair = "unique") 
#
Quads_sf <- Quads_raw %>% filter(Quarter == "Q1" | Quarter == "Q3")
#
## Survey SHs
SHs_raw <- read_excel("../Data/Srvy_data_clean_ELW.xlsx", sheet = "ShellHeights", 
                        skip = 0, col_names = TRUE,  
                        na = c("", "NULL", " ", "NAN", "na"), trim_ws = TRUE, 
                        .name_repair = "unique") 
#
```

# Data checks

```{r Data checks, echo = FALSE, results ="asis", fig.align='center', fig.dim=c(14, 8)}
#
cat("**FIXED STATIONS**")
cat("<br>Summary information:<br>")
Quads_sf %>% 
  filter(SrvyType == "Fixed") %>%
  group_by(Estuary) %>%
  summarise(Start = min(Year),
            End = max(Year)) %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything())
cat("<br>")
Quads_sf %>% 
  filter(SrvyType == "Fixed") %>%
  group_by(Estuary, Year, Quarter) %>%
  summarise(Quads = max(as.numeric(QuadratNumber))) %>%
  arrange(Year) %>%
  pivot_wider(names_from = Year, values_from = Quads) %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  sub_missing()
cat("<br>Notes: 
    <br> AB: Some surevys were less than 10 quads in 2015
    <br> 2007 BB, LX, LW, ML, SL, SR, TB counts performed for 1/4, 3/4, and 1 m2 quads, adjusted to fit schema: Quads 11-20 from 3/4, 21-30 from 1m2. 1-10 are 1/4m2")
cat("<br><br>*Check for empty data and small sample sizes within years and quarters.*<br>")
xtabs(~Estuary + Year, data = Quads_sf %>% filter(SrvyType == "Fixed")) %>% 
  as.data.frame() %>%
  pivot_wider(names_from = "Year", values_from = "Freq") %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything())
xtabs(~Estuary + Quarter, data = Quads_sf %>% filter(SrvyType == "Fixed")) %>% 
  as.data.frame() %>%
  pivot_wider(names_from = "Quarter", values_from = "Freq") %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything())
#
cat("<br><br>*Check station names belong to only one other factor level*.<br>
    <br>Check station names within each Estuary * Section <br>")
Quads_sf %>%
  filter(SrvyType == "Fixed") %>%
  distinct(Estuary, SectionName, StationName) %>%
  group_by(Estuary, SectionName) %>%
  summarise(
    nStations = n(),
    Stations = paste(sort(StationName), collapse = ", "),
    .groups = "drop"
  ) %>% 
  gt() 
cat("<br>Shared StationNames within Sections:<br>")
Quads_sf %>%
  filter(SrvyType == "Fixed") %>%
  distinct(StationName, SectionName) %>%
  count(StationName) %>%
  filter(n > 1) %>%
  gt()
cat("<br><br>")
cat("<br>Check section names within each Estuary <br>")
Quads_sf %>%
  filter(SrvyType == "Fixed") %>%
  distinct(Estuary, SectionName) %>%
  group_by(Estuary) %>%
  summarise(
    nStations = n(),
    Stations = paste(sort(SectionName), collapse = ", "),
    .groups = "drop"
  ) %>%
  gt()
cat("<br>Shared Sections across Estuaries.<br>")
Quads_sf %>%
  filter(SrvyType == "Fixed") %>%
  distinct(SectionName, Estuary) %>%
  count(SectionName) %>%
  filter(n > 1) %>%
  gt()
cat("<br>Section names should be updated to identify within/among estuaries.<br><br><br>")
#
cat("<br><br>*Check for outliers.*<br>")
ggplot(Quads_sf %>% filter(SrvyType == "Fixed"),
       aes(Year, TotalLive, color=Estuary)) +
    geom_boxplot() +
  lemon::facet_rep_grid(Estuary~., scales = "free_y")+
  ggtitle("Annual total live oysters")+
  theme_classic()+
  XYscales_dc
cat("<br>")
ggplot(Quads_sf %>% filter(SrvyType == "Fixed"),
       aes(Quarter, TotalLive, color=Estuary)) +
  geom_boxplot()+
  lemon::facet_rep_grid(Estuary~., scales = "free_y")+
  ggtitle("Quarterly total live oysters")+
  theme_classic()+
  XYscales_dc
cat("<br>")
ggplot(Quads_sf %>% filter(SrvyType == "Fixed"),
       aes(TotalLive)) +
  geom_histogram(binwidth=50)+
  ggtitle("Count of total live oysters")+
  theme_bw()+
  XYscales_cc
cat("<br><br>*Check distribution of data.*<br>")
meancheck <- mean((Quads_sf %>% filter(SrvyType == "Fixed"))$TotalLive, na.rm = T)
cat(paste("Mean: ", round(meancheck, 3), "<br>"))
varcheck <- var((Quads_sf %>% filter(SrvyType == "Fixed"))$TotalLive, na.rm = T)
cat(paste("Variance: ", round(varcheck, 3), "<br>"))
vmr <- varcheck / meancheck 
if(varcheck > meancheck && vmr > 1.1){
  cat("Variance is MUCH GREATER than the mean (Overdispersion detected): Negative binomial<br>")
  } else if (vmr >= 0.9 && vmr <= 1.1) {
    cat("Variance and mean are ALMOST EQUAL (Equidispersion): Poisson<br>")
    } else {
    cat("TRY: <br>
    many zeros: Zero-inflated negative binomial <br>
    Proporition: Binomial/beta<br>")
      }
cat("<br>
Remove BB samples since all data is 0s.
    <br>")

#
#
#Quads_raw %>% 
#  filter(SrvyType == "Fixed" & TotalLive >= 15000) %>%
#  dplyr::select(Date, Estuary, StationName, QuadratNumber, TotalLive:DeadRatio) %>%
#  arrange(desc(TotalLive))
#
#
#
```

```{r Data live count summaries, include=FALSE}

## Survey counts
Quads_df <- Quads_sf %>%
  # Remove BB samples
  filter(Estuary != "BB") %>%
  # Update for unique Sections
  mutate(Section = paste(Estuary, SectionName, sep = "-")) %>%
  # Group by all columns needed to keep
  group_by(Lab, SrvyType, 
           Date, Year, Month, Quarter,
           Estuary, Section, SectionName,
           StationName, StationNumber,
           QuadratNumber) %>%
  # Determine mean Live, Dead, and DeadRatio per Station
  summarise(Live = mean(TotalLive, na.rm = T),
            Dead = mean(TotalDead, na.rm = T),
            DeadRatio = mean(DeadRatio, na.rm = T),
            .groups = "drop") %>%
  # Factors
  mutate_at(c("Estuary", "Year", "Quarter", "Section", "SectionName", "StationName", "QuadratNumber"), as.factor)
#
#
#
## Mean survey counts per station (as rep) divided by Fixed or Random surveys
Fixed_counts <- Quads_df %>% 
  filter(SrvyType == "Fixed") 
#
Random_counts <- Quads_df %>% 
  filter(SrvyType == "Random")
#
### Annual summaries:
Fixed_Annual_summ <- Fixed_counts %>%
  # Group by all columns needed in data output
  group_by(Lab, Estuary, Year) %>%
  summarise(Samples = n(),
            # Live
            meanLive = mean(Live, na.rm = TRUE),
            sdLive = sd(Live, na.rm = TRUE),
            seLive   = sdLive / sqrt(n()),
            minLive = min(Live, na.rm = TRUE),
            maxLive = max(Live, na.rm = TRUE),
            .groups = "drop")
#
Random_Annual_summ <- Random_counts %>%
  # Group by all columns needed in data output
  group_by(Lab, Estuary, Year) %>%
  summarise(Samples = n(),
            # Live
            meanLive = mean(Live, na.rm = TRUE),
            sdLive = sd(Live, na.rm = TRUE),
            seLive   = sdLive / sqrt(n()),
            minLive = min(Live, na.rm = TRUE),
            maxLive = max(Live, na.rm = TRUE),
            .groups = "drop")
#
#
#
### Section summaries:
Fixed_Section_summ <- Fixed_counts %>%
  # Group by all columns needed in data output
  group_by(Lab, Estuary, Section) %>%
  summarise(Samples = n(),
            # Live
            meanLive = mean(Live, na.rm = TRUE),
            sdLive = sd(Live, na.rm = TRUE),
            seLive   = sdLive / sqrt(n()),
            minLive = min(Live, na.rm = TRUE),
            maxLive = max(Live, na.rm = TRUE),
            .groups = "drop")
#
Random_Section_summ <- Random_counts %>%
  # Group by all columns needed in data output
  group_by(Lab, Estuary, Section) %>%
  summarise(Samples = n(),
            # Live
            meanLive = mean(Live, na.rm = TRUE),
            sdLive = sd(Live, na.rm = TRUE),
            seLive   = sdLive / sqrt(n()),
            minLive = min(Live, na.rm = TRUE),
            maxLive = max(Live, na.rm = TRUE),
            .groups = "drop")
#
#
### Annual x Section summaries:
Fixed_Ann_Sec_summ <- Fixed_counts %>%
                   # Group by all columns needed in data output
                   group_by(Lab, Estuary, Year, Section) %>%
                   summarise(Samples = n(),
            # Live
            meanLive = mean(Live, na.rm = TRUE),
            sdLive = sd(Live, na.rm = TRUE),
            seLive   = sdLive / sqrt(n()),
            minLive = min(Live, na.rm = TRUE),
            maxLive = max(Live, na.rm = TRUE),
            .groups = "drop")
#
#
Random_Ann_Sec_summ <- Random_counts %>%
                   # Group by all columns needed in data output
                   group_by(Lab, Estuary, Year, Section) %>%
                   summarise(Samples = n(),
            # Live
            meanLive = mean(Live, na.rm = TRUE),
            sdLive = sd(Live, na.rm = TRUE),
            seLive   = sdLive / sqrt(n()),
            minLive = min(Live, na.rm = TRUE),
            maxLive = max(Live, na.rm = TRUE),
            .groups = "drop")
#
#
# 
#
#
#
```
\
\

# Background
Survey data limited to Q1 (Jan-Mar) and Q3 (Jul-Sep) for best comparison among sites. Surveys are divided by "Fixed" and "Random" for comparisons.\
Fixed = planned repeated sampling stations\
Random = single sampling event or station that is selected randomly for survey and has the potential for re-sampling if same station is selected across time\
Data is assessed at the quadrat level for comparisons.\
\

# Fixed location surveys
```{r Fixed Estuary annual table, echo = FALSE, results ="asis"}
cat("List of sites included:<br>")
cat(paste(unique(Fixed_Annual_summ$Estuary)))
#
Fixed_counts %>% ungroup() %>%
  dplyr::select(Estuary, Year) %>%
  group_by(Estuary, Year) %>%
  summarise(Count = n()) %>%
  arrange(Year) %>%
  pivot_wider(names_from = "Year", values_from = "Count") %>%
  ungroup()%>%
  gt() %>%
  sub_missing(missing_text = "")
#
#
```
\
\

## Statewide

```{r Fixed Estuary model comps, echo = FALSE, fig.align='center', results ="asis"}
#
# Estuary means
All_Fixed_summ <- Fixed_counts %>%
  # Group by all columns needed in data output
  group_by(Estuary) %>%
  summarise(Samples = n(),
            # Live
            meanLive = mean(Live, na.rm = TRUE),
            sdLive = sd(Live, na.rm = TRUE),
            seLive   = sdLive / sqrt(n()),
            minLive = min(Live, na.rm = TRUE),
            maxLive = max(Live, na.rm = TRUE),
            .groups = "drop")
#
# Annual means table
All_Fixed_summ %>%
  ungroup() %>%
  dplyr::select(Estuary,
                `Mean` = meanLive,
                `SE` = seLive) %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 2) %>% 
  tab_header(
    title = "Average live oyster density")
#
# Model data:
model_data <- Fixed_counts %>% 
  dplyr::select(Year, Quarter, Estuary, SectionName, StationNumber, QuadratNumber, Live) %>%
  drop_na() %>%
     mutate(SectionID = interaction(Estuary, SectionName, drop = TRUE),
            StationID = interaction(Estuary, SectionName, StationNumber, drop = TRUE),
            Year_n = as.integer(Year))
#
cat("<br>Check if zeros makes sense.<br>")
model_data %>%
  group_by(StationID) %>%
  summarise(
    n = n(),
    prop_zero = mean(Live == 0)
  ) %>%
  filter(prop_zero > 0.5) %>%
  arrange(desc(prop_zero)) %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything())
cat("<br>")
#
cat("<br><br>
  **Analyses:** <br>
    Fixed effects - Estuary, Quarter, Year (Except m6) <br>
    Random effects - Section, Station (sampling unit), Year (m6)<br>")
#
#
cat("<br>*Do estuaries differ after accounting for annual and seasonal variation and repeated sampling?*<br>")
set.seed(54321)
# Starting model
model1 <- suppressWarnings(
  glmmTMB::glmmTMB(Live ~ Estuary + Year + Quarter + (1|SectionID) + (1|StationID), 
                   family = nbinom2, data = model_data)
)
# Test zero-inflated
model2 <- suppressWarnings(
  glmmTMB::glmmTMB(Live ~ Estuary + Year + Quarter + (1|SectionID) + (1|StationID), 
                   ziformula = ~1,  family = nbinom2, data = model_data)
)
# Test 0s vary within Estuary and Quarter
model3 <- suppressWarnings(
  glmmTMB::glmmTMB(Live ~ Estuary + Year + Quarter + (1|SectionID) + (1|StationID), 
                   ziformula = ~Estuary + Quarter,  family = nbinom2, data = model_data)
)
# Test 0s vary within Estuary and Quarter with same temporal trend 
model4 <- suppressWarnings(
  glmmTMB::glmmTMB(Live ~ Estuary + Year_n + Quarter + (1|SectionID) + (1|StationID), 
                   ziformula = ~Estuary + Quarter,  family = nbinom2, data = model_data)
)
# Test 0s vary with Estuary and Quarter but Estuaries can have different seasonal trends
model5 <- suppressWarnings(
  glmmTMB::glmmTMB(Live ~ Estuary * Quarter + Year + (1|SectionID) + (1|StationID),
                   ziformula = ~ Estuary + Quarter, family = nbinom2, data = model_data)
)
# Test 0s vary within Estuary and Quarter but Estuaries can have different seasonal trends - Year as random effect
model6 <- suppressWarnings(
  glmmTMB::glmmTMB(Live ~ Estuary * Quarter + (1|Year) + (1|SectionID) + (1|StationID),
                   ziformula = ~ Estuary + Quarter, family = nbinom2, data = model_data)
)
#
cat("<br>**Compare models:**")
data.frame(
  Model_Name = c("Model 1", "Model 2", "Model 3", "Model 4", "Model 5", "Model 6"),
  Description = c("Starting model", 
                  "ZI model", 
                  "Zeros vary within Estuary and Quarter", 
                  "m3 + temporal trend", 
                  "m3 + estuaries can have different seasonal trends", 
                  "m5 but Year as random effect"),
  AIC        = c(AIC(model1), AIC(model2), AIC(model3), AIC(model4), AIC(model5), AIC(model6)),
  Formula    = c(deparse(formula(model1)), 
                 deparse(formula(model2)), 
                 deparse(formula(model3)), 
                 deparse(formula(model4)), 
                 deparse(formula(model5)), 
                 paste(deparse(formula(model6)), collapse = "")),
  ZI = c(deparse(formula(model1, component = "zi")), 
         deparse(formula(model2, component = "zi")), 
         deparse(formula(model3, component = "zi")), 
         deparse(formula(model4, component = "zi")), 
         deparse(formula(model5, component = "zi")), 
         deparse(formula(model6, component = "zi"))), 
  stringsAsFactors = FALSE
) %>% gt() %>% cols_align(align = c("center"), columns = c(3))
#
selectedModel <- rownames(AIC(model1, model2, model3, model4, model5, model6) %>% filter(AIC == min(AIC)))
#
cat("<br>The model with the lowest AIC is: ", print(selectedModel), "<br>")
#
#
```

```{r Fixed Estuary model assessment, echo = FALSE, fig.align='center', results ="asis"}
# Model assessment
#modelsummary(get(selectedModel),
#             shape = term ~ model + component,
#             stars = TRUE,
#             statistic = "(+/- {std.error}) <br> z = {statistic} <br> p = {p.value}",
#             metrics = c("AIC", "RMSE")) 
cat("<br> **Model assessment:**<br>
    Residuals:<br>")
sim <- DHARMa::simulateResiduals(get(selectedModel))
plot(sim)
cat("<br>")
cat("Overdispersion:<br>
    Dispersion ratio > 1 → overdispersion <br>
    Dispersion ratio < 1 → underdispersion <br><br>")
DHARMa::testDispersion(sim)
cat("<br>Underdispersion less concerning than overdispersion. Likely most explained by station variance.<br>")
cat("<br>")
DHARMa::testZeroInflation(sim)
cat("<br>")
temp <- DHARMa::testOutliers(sim)
temp$statistic
cat("<br>Parameter: ")
temp$parameter
cat("<br>p_value: ")
temp$p.value
cat("<br>Conf int: ")
temp$conf.int
cat("<br><br><br>")
#m1
model_tab <- car::Anova(model5, type = 2) %>%
  broom::tidy() %>% 
  as.data.frame() %>%
  mutate(statistic = round(statistic, 3),
         p.value = round(p.value, 3))
model_cld <- suppressMessages(
  suppressWarnings(
    left_join(All_Fixed_summ %>% 
                dplyr::select(-minLive, -maxLive), 
              multcomp::cld(
                emmeans(model5, ~ Estuary, type = "response"),
                Letters = letters, adjust = "tukey") %>%
                as.data.frame() %>%
                rename(Group = .group) %>%
                mutate(Group = stringr::str_trim(Group)) %>%
                dplyr::select(Estuary, Group))
    ))

p <- model_cld %>%
  ggplot(aes(Estuary, meanLive, fill = Group))+
  geom_bar(stat = "identity")+
  geom_errorbar(aes(ymin = meanLive, ymax = meanLive + seLive), width = 0.25)+
  geom_text(aes(y = meanLive + seLive, label = Group), vjust = -1, color = "black")+
  scale_x_discrete(expand = c(0.05,0.1))+
  scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
  scale_fill_viridis_d()+
  basetheme
# 
#
model_tab %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>% 
  tab_header(
    title = "Estuary model results")
p
#
## Summary info
model_mean <- All_Fixed_summ %>% ungroup() %>% 
  summarise(mean = mean(meanLive, na.rm = T),
            sd = sd(meanLive, na.rm = T))

pValue <- car::Anova(model5, type = 2) %>%
  broom::tidy() %>% 
  as.data.frame()
#
cat("<br><br>")
model_cld %>%
  left_join(All_Fixed_summ) %>%
  dplyr::select(-Group, everything(), Group) %>%
  gt() %>%
  fmt_number(
    columns = c(where(is.numeric), -Samples),
    decimals = 2
  ) %>%
  cols_align(
    align = "center",
    columns = everything()
  )
#
#
cat("<br><br>")
#
#
```

```{r Fixed Estuary model posthoc, echo = FALSE, fig.align='center', results ="asis"}
#
cat("<br> **Model post-hoc:**
    <br>Q: When accounting for the zero-inflation process, how does expected oyster abundance vary among Estuaries and Quarters? (Live ~ Estuary * Quarter + Year) > Estimated marginal mean live oyster abundance by estuary and quarter, with Tukey-adjusted pairwise comparisons.
    <br>Q: How does the probability of an additional/structural zero vary among Estuaries and Quarters? (ziformula = ~ Estuary + Quarter) > Estimated probability of a structural zero by estuary and quarter, with Tukey-adjusted pairwise comparisons.
    <br>*Is live abundance different among estuaries?*
    <br>Likelihood-ratio test
    <br>")
#
cat("<br><u>***Test Estuary effects***</u>:<br>")
m_noEstuary <- update(model5, . ~ . - Estuary - Estuary:Quarter)
anova(m_noEstuary, model5) %>% as.data.frame() %>% rownames_to_column() %>% gt()
cat("<br> p < 0.001. Estuary effect is significant = difference among estuaries.<br>")
#
cat("Mean data with groups:<br>")
model_cld %>%
  left_join(All_Fixed_summ) %>%
  dplyr::select(-Group, everything(), Group) %>%
  gt() %>%
  fmt_number(
    columns = c(where(is.numeric), -Samples),
    decimals = 2
  ) %>%
  cols_align(
    align = "center",
    columns = everything()
  )
cat("<br><br>*Estimated marginal means*: Adjusted means accounting for year, quarter, random effects, and zero-inflation.
    <br>")
confint(emmeans(model5, ~ Estuary, type = "response")) %>%
  as.data.frame() %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>%
  sub_missing()
confint(emmeans(model5, ~ Estuary, type = "response")) %>% 
  left_join(model_cld %>% dplyr::select(Estuary, Group)) %>%
  ggplot(aes(Estuary, response, color = Group))+
  geom_point(size = 4)+
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), width = 0.25, linewidth = 1) +
  geom_text(aes(y = asymp.UCL, label = Group), vjust = -0.75, size = 5, show.legend = FALSE)+
  basetheme + scale_x_discrete(expand =  c(0,0))+ 
  scale_y_continuous("Estimated mean live oysters/m2", expand = c(0,0),limits = c(0, 2500))+
  scale_color_viridis_d() + theme(legend.position = "none")
cat("<br><br>*Pairwise comparisons*: Correction for multiple comparisons.
    <br>")
pairs(emmeans(model5, ~ Estuary, type = "response"), adjust = "tukey") %>% 
  as.data.frame() %>% 
   mutate(
    Significance = case_when(
      p.value < 0.001 ~ "***",
      p.value < 0.01  ~ "**",
      p.value < 0.05  ~ "*",
      TRUE            ~ ""
    )
  ) %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>%
  sub_missing()
#
#
#
cat("<br><br><br><u>***Test Quarter effects***</u>:<br>")
m_noQuarter <- update(model5, . ~ . - Quarter - Estuary:Quarter)
anova(m_noQuarter, model5) %>% as.data.frame() %>% rownames_to_column() %>% gt()
cat("<br> p < 0.001. Quarter effect is significant = difference among quarters<br>")
#
cat("Mean data with groups:<br>")
Fixed_counts %>%
  # Group by all columns needed in data output
  group_by(Quarter) %>%
  summarise(Samples = n(),
            # Live
            meanLive = mean(Live, na.rm = TRUE),
            sdLive = sd(Live, na.rm = TRUE),
            seLive   = sdLive / sqrt(n()),
            .groups = "drop") %>%
  left_join( multcomp::cld(
                emmeans(model5, ~ Quarter, type = "response"),
                Letters = letters, adjust = "tukey") %>%
                as.data.frame() %>%
                rename(Group = .group) %>%
                mutate(Group = stringr::str_trim(Group)) %>%
                dplyr::select(Quarter, Group)) %>%
  dplyr::select(-Group, everything(), Group) %>%
  gt() %>%
  fmt_number(
    columns = c(where(is.numeric), -Samples),
    decimals = 2
  ) %>%
  cols_align(
    align = "center",
    columns = everything()
  )
cat("<br><br>*Estimated marginal means*: Adjusted means accounting for year, quarter, random effects, and zero-inflation.
    <br>")
confint(emmeans(model5, ~ Quarter, type = "response")) %>%
  as.data.frame() %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>%
  sub_missing()
cat("<br>")
confint(emmeans(model5, ~ Quarter, type = "response")) %>%
  left_join(multcomp::cld(emmeans(model5, ~ Quarter, type = "response"),
                Letters = letters, adjust = "tukey") %>%
                as.data.frame() %>%
                rename(Group = .group) %>%
                mutate(Group = stringr::str_trim(Group)) %>%
                dplyr::select(Quarter, Group)) %>%
  ggplot(aes(Quarter, response, color = Group))+
  geom_point(size = 4)+
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), width = 0.25) + 
  geom_text(aes(y = asymp.UCL, label = Group), vjust = -0.75, size = 5, show.legend = FALSE)+
  basetheme + scale_x_discrete(expand =  c(0.25,0))+ 
  scale_y_continuous("Estimated mean live oysters/m2", expand = c(0,0),limits = c(0, 400))+
  scale_color_viridis_d() + theme(legend.position = "none")
cat("<br><br>*Pairwise comparisons*: Correction for multiple comparisons.
    <br>")
pairs(emmeans(model5, ~ Quarter, type = "response"), adjust = "tukey") %>% 
  as.data.frame() %>% 
   mutate(
    Significance = case_when(
      p.value < 0.001 ~ "***",
      p.value < 0.01  ~ "**",
      p.value < 0.05  ~ "*",
      TRUE            ~ ""
    )
  ) %>% 
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>%
  sub_missing()
#
#
cat("<br><br><br><u>***Test interaction effects***</u>:<br>")
m_noInteraction <- update(model5, . ~ . - Estuary:Quarter)
anova(m_noInteraction, model5) %>% as.data.frame() %>% rownames_to_column() %>% gt()
cat("<br> p < 0.001. Interaction effect is significant = difference in quarters among estuaries.<br>")
#
#Plot
plot(
    emmeans(model5,
             ~ Quarter | Estuary,
             type="response")
)
#
cat("<br>Check differeneces among estuaries within quarter and within quarter among estuaries to best understand the interaction.<br><br>")
cat("*Estuary differences within Quarters*<br>")
cat("<br>Mean data with groups:<br>")
Fixed_counts %>%
  # Group by all columns needed in data output
  group_by(Quarter, Estuary) %>%
  summarise(Samples = n(),
            # Live
            meanLive = mean(Live, na.rm = TRUE),
            sdLive = sd(Live, na.rm = TRUE),
            seLive   = sdLive / sqrt(n()),
            .groups = "drop") %>%
  left_join( multcomp::cld(
                emmeans(model5, ~ Estuary|Quarter, type = "response"),
                Letters = letters, adjust = "tukey") %>%
                as.data.frame() %>%
                rename(Group = .group) %>%
                mutate(Group = stringr::str_trim(Group)) %>%
                dplyr::select(Estuary, Quarter, Group)) %>%
  dplyr::select(-Group, everything(), Group) %>%
  gt() %>%
  fmt_number(
    columns = c(where(is.numeric), -Samples),
    decimals = 2
  ) %>%
  cols_align(
    align = "center",
    columns = everything()
  )
cat("<br><br>*Estimated marginal means*: Adjusted means accounting for year, random effects, and zero-inflation.
    <br>")
confint(emmeans(model5, ~ Estuary|Quarter, type = "response")) %>%
  as.data.frame() %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>%
  sub_missing()
cat("<br>")
confint(emmeans(model5, ~ Estuary|Quarter, type = "response")) %>%
  left_join( multcomp::cld(
                emmeans(model5, ~ Estuary|Quarter, type = "response"),
                Letters = letters, adjust = "tukey") %>%
                as.data.frame() %>%
                rename(Group = .group) %>%
                mutate(Group = stringr::str_trim(Group)) %>%
                dplyr::select(Estuary, Quarter, Group)) %>%
  ggplot(aes(Estuary, response, color = Estuary))+
  geom_point(size = 5)+
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), width = 0.25, linewdith = 1.5)+
  geom_text(aes(y = asymp.UCL, label = Group), vjust = -0.75, size = 5, show.legend = FALSE)+
  lemon::facet_rep_grid(.~Quarter)+
  basetheme + scale_x_discrete(expand =  c(0.05,0))+ 
  scale_y_continuous("Estimated mean live oysters/m2", expand = c(0,0),limits = c(0, 2500))+
    scale_color_viridis_d() + theme(legend.position = "none")
cat("<br><br>*Pairwise comparisons*: Correction for multiple comparisons.
    <br>")
pairs(emmeans(model5, ~ Estuary|Quarter, type = "response"), adjust = "tukey") %>% 
  as.data.frame() %>% 
   mutate(
    Significance = case_when(
      p.value < 0.001 ~ "***",
      p.value < 0.01  ~ "**",
      p.value < 0.05  ~ "*",
      TRUE            ~ ""
    )
  ) %>% 
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>%
  sub_missing()
#
cat("<br><br>")
cat("*Quarter differences within Estuaries*<br>")
cat("<br>Mean data with groups:<br>")
Fixed_counts %>%
  # Group by all columns needed in data output
  group_by(Estuary, Quarter) %>%
  summarise(Samples = n(),
            # Live
            meanLive = mean(Live, na.rm = TRUE),
            sdLive = sd(Live, na.rm = TRUE),
            seLive   = sdLive / sqrt(n()),
            .groups = "drop") %>%
  left_join( multcomp::cld(
                emmeans(model5, ~ Quarter|Estuary, type = "response"),
                Letters = letters, adjust = "tukey") %>%
                as.data.frame() %>%
                rename(Group = .group) %>%
                mutate(Group = stringr::str_trim(Group)) %>%
                dplyr::select(Quarter, Estuary, Group)) %>%
  dplyr::select(-Group, everything(), Group) %>%
  gt() %>%
  fmt_number(
    columns = c(where(is.numeric), -Samples),
    decimals = 2
  ) %>%
  cols_align(
    align = "center",
    columns = everything()
  )
cat("<br><br>*Estimated marginal means*: Adjusted means accounting for year, random effects, and zero-inflation.
    <br>")
confint(emmeans(model5, ~ Quarter|Estuary, type = "response")) %>%
  as.data.frame() %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>%
  sub_missing()
cat("<br>")
confint(emmeans(model5, ~ Quarter|Estuary, type = "response")) %>%
  ggplot(aes(Quarter, response, color = Quarter))+
  geom_point(size = 5)+
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), width = 0.25, linewdith = 1.5) + 
  lemon::facet_rep_grid(.~Estuary)+
  basetheme + scale_x_discrete(expand =  c(0.15,0))+ 
  scale_y_continuous("Estimated marginal means", expand = c(0,0),limits = c(0, 2000))+
  scale_color_viridis_d()
cat("<br><br>*Pairwise comparisons*: Correction for multiple comparisons.
    <br>")
pairs(emmeans(model5, ~ Quarter|Estuary, type = "response"), adjust = "tukey") %>% 
  as.data.frame() %>% 
   mutate(
    Significance = case_when(
      p.value < 0.001 ~ "***",
      p.value < 0.01  ~ "**",
      p.value < 0.05  ~ "*",
      TRUE            ~ ""
    )
  ) %>% 
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>%
  sub_missing()
#
#
#
#
cat("<br><br><br><u>***Test zero-inflation effects***</u>:<br>")
cat("<br>*Do estuaries differ in their probability of being a 0?*<br>")
cat("<br><br>*Estimated marginal means*: Adjusted means.
    <br>")
confint(emmeans(model5, ~ Estuary, component = "zi", type = "response")) %>%
  as.data.frame() %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>%
  sub_missing()
cat("<br>")
confint(emmeans(model5, ~ Estuary, component = "zi", type = "response")) %>%
  ggplot(aes(Estuary, response))+
  geom_point(size = 4)+
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), width = 0.25) + 
  basetheme + scale_x_discrete(expand =  c(0.25,0))+ 
  scale_y_continuous("Estimated marginal means", expand = c(0,0),limits = c(0, 0.5))
cat("<br><br>*Pairwise comparisons*: Correction for multiple comparisons.
    <br>")
pairs(emmeans(model5, ~ Estuary, component = "zi", type = "response"), adjust = "tukey") %>% 
  as.data.frame() %>% 
   mutate(
    Significance = case_when(
      p.value < 0.001 ~ "***",
      p.value < 0.01  ~ "**",
      p.value < 0.05  ~ "*",
      TRUE            ~ ""
    )
  ) %>% 
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>%
  sub_missing()
#
cat("<br>")
cat("<br>*Do quarters differ in their probability of being a 0?*<br>")
cat("<br><br>*Estimated marginal means*: Adjusted means.
    <br>")
confint(emmeans(model5, ~ Quarter, component = "zi", type = "response")) %>%
  as.data.frame() %>%
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>%
  sub_missing()
cat("<br>")
confint(emmeans(model5, ~ Quarter, component = "zi", type = "response")) %>%
  ggplot(aes(Quarter, response))+
  geom_point(size = 4)+
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), width = 0.25) + 
  basetheme + scale_x_discrete(expand =  c(0.25,0))+ 
  scale_y_continuous("Estimated marginal means", expand = c(0,0),limits = c(0, 0.25))
cat("<br><br>*Pairwise comparisons*: Correction for multiple comparisons.
    <br>")
pairs(emmeans(model5, ~ Quarter, component = "zi", type = "response"), adjust = "tukey") %>% 
  as.data.frame() %>% 
   mutate(
    Significance = case_when(
      p.value < 0.001 ~ "***",
      p.value < 0.01  ~ "**",
      p.value < 0.05  ~ "*",
      TRUE            ~ ""
    )
  ) %>% 
  gt() %>%
  cols_align(align = c("center"), columns = everything()) %>%
  fmt_number(
    decimals = 3) %>%
  sub_missing()
#
#
cat("<br><br><br><br>") 
#
#
#
```

```{r Fixed estaury model comps, echo = FALSE, results='asis', fig.align='center'}
#
#

#
#m3 outlier n.s., dispersion 0.04, KS 0, zi 1.0535 p = 0.008 
#m5 outlier n.s., dispersion 0.024, KS 0, zi 1.0554 p = 0.016 
#
```
\
**Summary:**
The mean number of live oysters surveyed ranged from 
`r round((All_Fixed_summ %>% slice_min(meanLive, n = 1, with_ties = T))$meanLive,1)` 
oysters/m2 in 
`r (All_Fixed_summ %>% slice_min(meanLive, n = 1, with_ties = T))$Estuary` 
to 
`r round((All_Fixed_summ %>% slice_max(meanLive, n = 1, with_ties = T))$meanLive,1)` 
oysters/m2 in 
`r (All_Fixed_summ %>% slice_max(meanLive, n = 1, with_ties = T))$Estuary` 
with an overall average of 
`r round(model_mean$mean,1)` 
+/- 
`r round(model_mean$sd, 1)` 
oysters/m2. Mean live oyster density 
`r if(!is.null(pValue) && pValue$p.value[2] < 0.5){paste("varied significantly")} else {paste("did not vary significantly")}` 
among estuaries 
`r if(!is.null(pValue) && pValue$p.value[2] < 0.001){paste("(p < 0.001)")} else if(is.null(pValue)){""} else {paste0("(p = ",round(pValue$p.value[2], 3), ")")}`.
\
\

```{r All estuaries annual plot,  echo = FALSE, fig.align='center', results='asis'}
Fixed_Annual_summ %>%
  group_by(Year, Estuary) %>%
  summarise(mean = mean(meanLive, na.rm = T),
            sd = sd(meanLive, na.rm = T)) %>%
  ggplot(aes(Year, mean, group = Estuary))+
  geom_line(aes(color = Estuary), linewidth = 1.5)+
  scale_x_discrete(expand = c(0.01,0.1))+
  scale_y_continuous("Average live oysters per m2", limits = c(0, NA), expand = expansion(mult = c(0,0.05)))+
  scale_colour_viridis_d(option = "H")+
  ggtitle("Annual mean oysters/m2 per estuary")+
  basetheme + theme(axis.text.x = element_text(angle = 45))
cat("<br><br>")
```
